---
title: "Ant Climate Project"
subtitle: "Path analysis: Tropical vs Temperate vs Both"
author: "Louis Bell-Roberts"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
    includes:  
      in_header: preamble-latex.tex
urlcolor: blue
date: \today
---

\tableofcontents
\newpage 

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F, fig.align='center')
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = T)
# Packages
library(data.table)
library(ape)
library(ggtree) ## Basic ggplot package for trees
library(ggtreeExtra) ## For fancy tree plotting
library(ufs) ## For ggqq plot
library(phylolm)
library(rr2)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(phylopath)
library(phylolm)
library(phytools)
theme_set(theme_minimal())
library(kableExtra)
library(stringr)
# global plotting options for histogram
xmin= -7.5
xmax= 0
```

Initial comments:

Read in the ant data and prepare the variables for path analysis. There are 474 species (116 Tropical, 190 for Temperate and 168 for 'Both') for which data is available for colony size and climatic variables, excluding special ants. 
```{r Read in ant data for both tropical and other}
ant_data_tropical<- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/Tropical_ant_data.csv")
ant_data_temperate<- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/Temperate_ant_data_230804.csv")
ant_data_both<- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/Both_ant_data_230804.csv")

#Assign rownames as species names
rownames(ant_data_tropical) <- ant_data_tropical$valid_species_name
rownames(ant_data_temperate) <- ant_data_temperate$valid_species_name
rownames(ant_data_both) <- ant_data_both$valid_species_name

#Log transform colony size variable
ant_data_tropical$colony.size.y <- log10(ant_data_tropical$colony.size.y)
ant_data_temperate$colony.size.y <- log10(ant_data_temperate$colony.size.y)
ant_data_both$colony.size.y <- log10(ant_data_both$colony.size.y)

#Square root transform PREavg_avg variable
ant_data_tropical$PREavg_avg <- sqrt(ant_data_tropical$PREavg_avg)
ant_data_temperate$PREavg_avg <- sqrt(ant_data_temperate$PREavg_avg)
ant_data_both$PREavg_avg <- sqrt(ant_data_both$PREavg_avg)

#Assign Poly_id as a factor
ant_data_tropical$poly_id <- as.factor(ant_data_tropical$poly_id)
ant_data_temperate$poly_id <- as.factor(ant_data_temperate$poly_id)
ant_data_both$poly_id <- as.factor(ant_data_both$poly_id)

#Read in trees
##Tropical species trees
tropical_anttree_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_stem_tropical_pruned_MCC.tre")
tropical_anttree_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_crown_tropical_pruned_MCC.tre")
tropical_anttree_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_stem_tropical_pruned_MCC.tre")
tropical_anttree_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_crown_tropical_pruned_MCC.tre")

##Temperate species trees
temperate_anttree_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_stem_temperate_pruned_MCC.tre")
temperate_anttree_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_crown_temperate_pruned_MCC.tre")
temperate_anttree_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_stem_temperate_pruned_MCC.tre")
temperate_anttree_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_crown_temperate_pruned_MCC.tre")

##Both species trees
both_anttree_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_stem_both_pruned_MCC.tre")
both_anttree_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_crown_both_pruned_MCC.tre")
both_anttree_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_stem_both_pruned_MCC.tre")
both_anttree_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_crown_both_pruned_MCC.tre")

#Select columns of interest
##Tropical - PREavg and TMPavg
ant_data_tropical_PREavg_selected <- ant_data_tropical %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PREavg_avg)
ant_data_tropical_TMPavg_selected <- ant_data_tropical %>% dplyr::select(valid_species_name, poly_id, colony.size.y, TMPavg_avg)


##Temperate - PREavg and TMPavg
ant_data_temperate_PREavg_selected <- ant_data_temperate %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PREavg_avg)
ant_data_temperate_TMPavg_selected <- ant_data_temperate %>% dplyr::select(valid_species_name, poly_id, colony.size.y, TMPavg_avg)

##Both - PREavg and TMPavg
ant_data_both_PREavg_selected <- ant_data_both %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PREavg_avg)
ant_data_both_TMPavg_selected <- ant_data_both %>% dplyr::select(valid_species_name, poly_id, colony.size.y, TMPavg_avg)

#Rename the variables used in the analysis
##Tropical - PREavg and TMPavg
ant_data_tropical_PREavg_selected_named <- ant_data_tropical_PREavg_selected %>% 
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         PREavg=PREavg_avg)
ant_data_tropical_TMPavg_selected_named <- ant_data_tropical_TMPavg_selected %>% 
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         TMPavg=TMPavg_avg)

##Temperate - PREavg and TMPavg
ant_data_temperate_PREavg_selected_named <- ant_data_temperate_PREavg_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         PREavg=PREavg_avg)
ant_data_temperate_TMPavg_selected_named <- ant_data_temperate_TMPavg_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         TMPavg=TMPavg_avg)

##Both - PREavg and TMPavg
ant_data_both_PREavg_selected_named <- ant_data_both_PREavg_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         PREavg=PREavg_avg)
ant_data_both_TMPavg_selected_named <- ant_data_both_TMPavg_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         TMPavg=TMPavg_avg)
```

When more than on climatic variable is present in the best model (based on AIC model selection), we divide the path analysis into multiple different analyses. This is because path analysis would not accept having more than one climatic predictor in the analysis because the linear models produced had highly significant relationships between the multiple climatic predictors being analysed. The potential model set is reduced to just four models for each analysis, based on all of the possible models given that colony size has a direct effect on the number of worker castes.

# Summary

## PRE
- Path analysis not necessary for tropical regions as 'phylogeny-only' model is best
- In temperate regions, greater colony size favours both greater worker size variation and allows invasion into drier regions. Both path coefficients are significant.
- In species that occur in both regions, greater worker size variation allows invasion into drier regions and drier climates favour greater colony size. However, neither of these paths are significant.

## TMP
- No significant paths between TMP and either colony size or variation in worker size.

# PRE

## Tropical
### Alternative causal models
```{r Tropical - Define the potential causal models PREavg, fig.width=8, fig.height=4}
### The final set of path models ###
#Define the models for the analysis: response before the ~, effector after the ~

tropical_PREavg_models <- define_model_set(
  one = c(Poly_id ~ PREavg, Poly_id ~ Colony_size),
  two = c(PREavg ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ PREavg, Poly_id ~ Colony_size),
  four = c(PREavg ~ Colony_size, Poly_id ~ Colony_size)
)

#PREavg model set - 4 models
plot_model_set(tropical_PREavg_models, box_x = 22, box_y = 8, text_size = 3.5)
```

### Path analysis
```{r Tropical - Analyse models PREavg, fig.width=14, fig.height=6}
#Run the models on each of the 4 different MCC trees (changing model of evolution does have effect on outcome, even though phyloglm doesn't have a 'method' option, while phylolm does)
tropical_PREavg_result_NCuniform_stem <- phylo_path(tropical_PREavg_models, data = ant_data_tropical_PREavg_selected_named, tree = tropical_anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
tropical_PREavg_result_NCuniform_crown <- phylo_path(tropical_PREavg_models, data = ant_data_tropical_PREavg_selected_named, tree = tropical_anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
tropical_PREavg_result_FBD_stem <- phylo_path(tropical_PREavg_models, data = ant_data_tropical_PREavg_selected_named, tree = tropical_anttree_FBD_stem, model = "lambda", method = "logistic_MPLE")
tropical_PREavg_result_FBD_crown <- phylo_path(tropical_PREavg_models, data = ant_data_tropical_PREavg_selected_named, tree = tropical_anttree_FBD_crown, model = "lambda", method = "logistic_MPLE")

#Summarise the models
tropical_PREavg_result_NCuniform_stem_summary <- tropical_PREavg_result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(tropical_PREavg_result_NCuniform_stem_summary) <- NULL

tropical_PREavg_result_NCuniform_crown_summary <- tropical_PREavg_result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(tropical_PREavg_result_NCuniform_crown_summary) <- NULL

tropical_PREavg_result_FBD_stem_summary <- tropical_PREavg_result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(tropical_PREavg_result_FBD_stem_summary) <- NULL

tropical_PREavg_result_FBD_crown_summary <- tropical_PREavg_result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(tropical_PREavg_result_FBD_crown_summary) <- NULL

#Produce tables for Rmarkdown
kable(tropical_PREavg_result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position") #The kableExtra chunk of code holds the table in position so that it does not start floating around the document
kable(tropical_PREavg_result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(tropical_PREavg_result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(tropical_PREavg_result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")

#Plot model summaries
# plot(summary(tropical_PREavg_result_NCuniform_stem))
# plot(summary(tropical_PREavg_result_NCuniform_crown))
# plot(summary(tropical_PREavg_result_FBD_stem))
# plot(summary(tropical_PREavg_result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage 
tropical_PREavg_average_model_full_NCuniform_stem <- average(tropical_PREavg_result_NCuniform_stem, avg_method = "full")
tropical_PREavg_average_model_full_NCuniform_crown <- average(tropical_PREavg_result_NCuniform_crown, avg_method = "full")
tropical_PREavg_average_model_full_FBD_stem <- average(tropical_PREavg_result_FBD_stem, avg_method = "full")
tropical_PREavg_average_model_full_FBD_crown <- average(tropical_PREavg_result_FBD_crown, avg_method = "full")

# PREavg_average_model <- average(PREavg_result, avg_method = 'conditional') #no 'shrinkage'
plot(tropical_PREavg_average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(tropical_PREavg_average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(tropical_PREavg_average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(tropical_PREavg_average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
```

## Temperate

### Alternative causal models
```{r Temperate - Define the potential causal models PREavg, fig.width=10, fig.height=6}
temperate_PREavg_models <- define_model_set(
  one = c(Poly_id ~ PREavg, Poly_id ~ Colony_size),
  two = c(PREavg ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ PREavg, Poly_id ~ Colony_size),
  four = c(PREavg ~ Colony_size, Poly_id ~ Colony_size)
)

#PRE model set - 4 models
plot_model_set(temperate_PREavg_models, box_x = 22, box_y = 8, text_size = 3.5)

```

### Path analysis
```{r Temperate - Analyse models PREavg, fig.width=14, fig.height=6}
#Run the models on each of the 4 different MCC trees
temperate_PREavg_result_NCuniform_stem <- phylo_path(temperate_PREavg_models, data = ant_data_temperate_PREavg_selected_named, tree = temperate_anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
temperate_PREavg_result_NCuniform_crown  <- phylo_path(temperate_PREavg_models, data = ant_data_temperate_PREavg_selected_named, tree = temperate_anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
temperate_PREavg_result_FBD_stem <- phylo_path(temperate_PREavg_models, data = ant_data_temperate_PREavg_selected_named, tree = temperate_anttree_FBD_stem, model = "lambda", method = "logistic_MPLE")
temperate_PREavg_result_FBD_crown <- phylo_path(temperate_PREavg_models, data = ant_data_temperate_PREavg_selected_named, tree = temperate_anttree_FBD_crown, model = "lambda", method = "logistic_MPLE")


#Summarise the models
temperate_PREavg_result_NCuniform_stem_summary <- temperate_PREavg_result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_PREavg_result_NCuniform_stem_summary) <- NULL

temperate_PREavg_result_NCuniform_crown_summary <- temperate_PREavg_result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_PREavg_result_NCuniform_crown_summary) <- NULL

temperate_PREavg_result_FBD_stem_summary <- temperate_PREavg_result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_PREavg_result_FBD_stem_summary) <- NULL

temperate_PREavg_result_FBD_crown_summary <- temperate_PREavg_result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_PREavg_result_FBD_crown_summary) <- NULL

#Produce tables for Rmarkdown
kable(temperate_PREavg_result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position") #The kableExtra chunk of code holds the table in position so that it does not start floating around the document
kable(temperate_PREavg_result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(temperate_PREavg_result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(temperate_PREavg_result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")

# #Plot model summaries
# plot(summary(temperate_PREavg_result_NCuniform_stem))
# plot(summary(temperate_PREavg_result_NCuniform_crown))
# plot(summary(temperate_PREavg_result_FBD_stem))
# plot(summary(temperate_PREavg_result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage
temperate_PREavg_average_model_full_NCuniform_stem <- average(temperate_PREavg_result_NCuniform_stem, avg_method = "full")
temperate_PREavg_average_model_full_NCuniform_crown <- average(temperate_PREavg_result_NCuniform_crown, avg_method = "full")
temperate_PREavg_average_model_full_FBD_stem <- average(temperate_PREavg_result_FBD_stem, avg_method = "full")
temperate_PREavg_average_model_full_FBD_crown <- average(temperate_PREavg_result_FBD_crown, avg_method = "full")

# TMPsd_average_model <- average(TMPsd_result, avg_method = 'conditional') #no 'shrinkage'
plot(temperate_PREavg_average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(temperate_PREavg_average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(temperate_PREavg_average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(temperate_PREavg_average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
```

#### Estimate confidence intervals for path coefficients
```{r Temperate - PRE path coefficients CI, fig.width=14, fig.height=2}
#Estimate confidence intervals for path coefficients
##NCuniform_stem
# temperate_PREavg_CI_four_NCuniform_stem <- choice(temperate_PREavg_result_NCuniform_stem, "four", boot = 500)
# 
# ##NCuniform_crown
# temperate_PREavg_CI_four_NCuniform_crown <- choice(temperate_PREavg_result_NCuniform_crown, "four", boot = 500)
# 
# ##FBD_stem
# temperate_PREavg_CI_four_FBD_stem <- choice(temperate_PREavg_result_FBD_stem, "four", boot = 500)
# 
# ##FBD_crown
# temperate_PREavg_CI_four_FBD_crown <- choice(temperate_PREavg_result_FBD_crown, "four", boot = 500)

#Print out the tables and plots
##NCuniform_stem
###Individual models
# temperate_PREavg_CI_four_NCuniform_stem

###Averaged model
coef_plot(temperate_PREavg_average_model_full_NCuniform_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##NCuniform_crown
###Individual models
# temperate_PREavg_CI_four_NCuniform_crown

###Averaged model
coef_plot(temperate_PREavg_average_model_full_NCuniform_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_stem
###Individual models
# temperate_PREavg_CI_four_FBD_stem
###Averaged model
coef_plot(temperate_PREavg_average_model_full_FBD_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_crown
###Individual models
# temperate_PREavg_CI_four_FBD_crown

###Averaged model
coef_plot(temperate_PREavg_average_model_full_FBD_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

## Both

### Alternative causal models
```{r Both - Define the potential causal models PREavg, fig.width=10, fig.height=6}
both_PREavg_models <- define_model_set(
  one = c(Poly_id ~ PREavg, Poly_id ~ Colony_size),
  two = c(PREavg ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ PREavg, Poly_id ~ Colony_size),
  four = c(PREavg ~ Colony_size, Poly_id ~ Colony_size)
)

#PRE model set - 4 models
plot_model_set(both_PREavg_models, box_x = 22, box_y = 8, text_size = 3.5)

```

### Path analysis

```{r Both - Analyse models PREavg, fig.width=14, fig.height=6}
#Run the models on each of the 4 different MCC trees
both_PREavg_result_NCuniform_stem <- phylo_path(both_PREavg_models, data = ant_data_both_PREavg_selected_named, tree = both_anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
both_PREavg_result_NCuniform_crown  <- phylo_path(both_PREavg_models, data = ant_data_both_PREavg_selected_named, tree = both_anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
both_PREavg_result_FBD_stem <- phylo_path(both_PREavg_models, data = ant_data_both_PREavg_selected_named, tree = both_anttree_FBD_stem, model = "lambda", method = "logistic_MPLE")
both_PREavg_result_FBD_crown <- phylo_path(both_PREavg_models, data = ant_data_both_PREavg_selected_named, tree = both_anttree_FBD_crown, model = "lambda", method = "logistic_MPLE")


#Summarise the models
both_PREavg_result_NCuniform_stem_summary <- both_PREavg_result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_PREavg_result_NCuniform_stem_summary) <- NULL

both_PREavg_result_NCuniform_crown_summary <- both_PREavg_result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_PREavg_result_NCuniform_crown_summary) <- NULL

both_PREavg_result_FBD_stem_summary <- both_PREavg_result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_PREavg_result_FBD_stem_summary) <- NULL

both_PREavg_result_FBD_crown_summary <- both_PREavg_result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_PREavg_result_FBD_crown_summary) <- NULL

#Produce tables for Rmarkdown
kable(both_PREavg_result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position") #The kableExtra chunk of code holds the table in position so that it does not start floating around the document
kable(both_PREavg_result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(both_PREavg_result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(both_PREavg_result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")

# #Plot model summaries
# plot(summary(both_PREavg_result_NCuniform_stem))
# plot(summary(both_PREavg_result_NCuniform_crown))
# plot(summary(both_PREavg_result_FBD_stem))
# plot(summary(both_PREavg_result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage
both_PREavg_average_model_full_NCuniform_stem <- average(both_PREavg_result_NCuniform_stem, avg_method = "full")
both_PREavg_average_model_full_NCuniform_crown <- average(both_PREavg_result_NCuniform_crown, avg_method = "full")
both_PREavg_average_model_full_FBD_stem <- average(both_PREavg_result_FBD_stem, avg_method = "full")
both_PREavg_average_model_full_FBD_crown <- average(both_PREavg_result_FBD_crown, avg_method = "full")

# TMPsd_average_model <- average(TMPsd_result, avg_method = 'conditional') #no 'shrinkage'
plot(both_PREavg_average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(both_PREavg_average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(both_PREavg_average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(both_PREavg_average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
```

#### Estimate confidence intervals for path coefficients
```{r Both - PRE path coefficients CI, fig.width=19, fig.height=2}
#Estimate confidence intervals for path coefficients
##NCuniform_stem
both_PREavg_CI_three_NCuniform_stem <- choice(both_PREavg_result_NCuniform_stem, "three", boot = 500)
both_PREavg_CI_two_NCuniform_stem <- choice(both_PREavg_result_NCuniform_stem, "two", boot = 500)
# 
# ##NCuniform_crown
# both_PREavg_CI_three_NCuniform_crown <- choice(both_PREavg_result_NCuniform_crown, "three", boot = 500)
# both_PREavg_CI_two_NCuniform_crown <- choice(both_PREavg_result_NCuniform_crown, "two", boot = 500)
# 
# ##FBD_stem
# both_PREavg_CI_three_FBD_stem <- choice(both_PREavg_result_FBD_stem, "three", boot = 500)
# both_PREavg_CI_two_FBD_stem <- choice(both_PREavg_result_FBD_stem, "two", boot = 500)
# 
# ##FBD_crown
# both_PREavg_CI_three_FBD_crown <- choice(both_PREavg_result_FBD_crown, "three", boot = 500)
# both_PREavg_CI_two_FBD_crown <- choice(both_PREavg_result_FBD_crown, "two", boot = 500)

#Print out the tables and plots
##NCuniform_stem
###Individual models
# both_PREavg_CI_three_NCuniform_stem
# both_PREavg_CI_two_NCuniform_stem

###Averaged model
coef_plot(both_PREavg_average_model_full_NCuniform_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##NCuniform_crown
###Individual models
# both_PREavg_CI_three_NCuniform_crown
# both_PREavg_CI_two_NCuniform_crown
###Averaged model
coef_plot(both_PREavg_average_model_full_NCuniform_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_stem
###Individual models
# both_PREavg_CI_three_FBD_stem
# both_PREavg_CI_two_FBD_stem
###Averaged model
coef_plot(both_PREavg_average_model_full_FBD_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_crown
###Individual models
# both_PREavg_CI_three_FBD_crown
# both_PREavg_CI_two_FBD_crown
###Averaged model
coef_plot(both_PREavg_average_model_full_FBD_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

# TMP

## Temperate

### Alternative causal models
```{r Temperate - Define the potential causal models TMPavg, fig.width=10, fig.height=6}
temperate_TMPavg_models <- define_model_set(
  one = c(Poly_id ~ TMPavg, Poly_id ~ Colony_size),
  two = c(TMPavg ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ TMPavg, Poly_id ~ Colony_size),
  four = c(TMPavg ~ Colony_size, Poly_id ~ Colony_size)
)

#TMP model set - 4 models
plot_model_set(temperate_TMPavg_models, box_x = 22, box_y = 8, text_size = 3.5)

```

### Path analysis
```{r Temperate - Analyse models TMPavg, fig.width=14, fig.height=5}
#Run the models on each of the 4 different MCC trees
temperate_TMPavg_result_NCuniform_stem <- phylo_path(temperate_TMPavg_models, data = ant_data_temperate_TMPavg_selected_named, tree = temperate_anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
temperate_TMPavg_result_NCuniform_crown  <- phylo_path(temperate_TMPavg_models, data = ant_data_temperate_TMPavg_selected_named, tree = temperate_anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
temperate_TMPavg_result_FBD_stem <- phylo_path(temperate_TMPavg_models, data = ant_data_temperate_TMPavg_selected_named, tree = temperate_anttree_FBD_stem, model = "lambda", method = "logistic_MPLE")
temperate_TMPavg_result_FBD_crown <- phylo_path(temperate_TMPavg_models, data = ant_data_temperate_TMPavg_selected_named, tree = temperate_anttree_FBD_crown, model = "lambda", method = "logistic_MPLE")


#Summarise the models
temperate_TMPavg_result_NCuniform_stem_summary <- temperate_TMPavg_result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_TMPavg_result_NCuniform_stem_summary) <- NULL

temperate_TMPavg_result_NCuniform_crown_summary <- temperate_TMPavg_result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_TMPavg_result_NCuniform_crown_summary) <- NULL

temperate_TMPavg_result_FBD_stem_summary <- temperate_TMPavg_result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_TMPavg_result_FBD_stem_summary) <- NULL

temperate_TMPavg_result_FBD_crown_summary <- temperate_TMPavg_result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(temperate_TMPavg_result_FBD_crown_summary) <- NULL

#Produce tables for Rmarkdown
kable(temperate_TMPavg_result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position") #The kableExtra chunk of code holds the table in position so that it does not start floating around the document
kable(temperate_TMPavg_result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(temperate_TMPavg_result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(temperate_TMPavg_result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")

# #Plot model summaries
# plot(summary(temperate_TMPavg_result_NCuniform_stem))
# plot(summary(temperate_TMPavg_result_NCuniform_crown))
# plot(summary(temperate_TMPavg_result_FBD_stem))
# plot(summary(temperate_TMPavg_result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage
temperate_TMPavg_average_model_full_NCuniform_stem <- average(temperate_TMPavg_result_NCuniform_stem, avg_method = "full")
temperate_TMPavg_average_model_full_NCuniform_crown <- average(temperate_TMPavg_result_NCuniform_crown, avg_method = "full")
temperate_TMPavg_average_model_full_FBD_stem <- average(temperate_TMPavg_result_FBD_stem, avg_method = "full")
temperate_TMPavg_average_model_full_FBD_crown <- average(temperate_TMPavg_result_FBD_crown, avg_method = "full")

# TMPsd_average_model <- average(TMPsd_result, avg_method = 'conditional') #no 'shrinkage'
plot(temperate_TMPavg_average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(temperate_TMPavg_average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(temperate_TMPavg_average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(temperate_TMPavg_average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
```
#### Estimate confidence intervals for path coefficients
```{r Temperate - TMP path coefficients CI, fig.width=14, fig.height=2}
#Estimate confidence intervals for path coefficients
##NCuniform_stem
# temperate_TMPavg_CI_one_NCuniform_stem <- choice(temperate_TMPavg_result_NCuniform_stem, "one", boot = 500)
# 
# ##NCuniform_crown
# temperate_TMPavg_CI_one_NCuniform_crown <- choice(temperate_TMPavg_result_NCuniform_crown, "one", boot = 500)
# 
# ##FBD_stem
# temperate_TMPavg_CI_one_FBD_stem <- choice(temperate_TMPavg_result_FBD_stem, "one", boot = 500)
# 
# ##FBD_crown
# temperate_TMPavg_CI_one_FBD_crown <- choice(temperate_TMPavg_result_FBD_crown, "one", boot = 500)
# temperate_TMPavg_CI_three_FBD_crown <- choice(temperate_TMPavg_result_FBD_crown, "three", boot = 500)

#Print out the tables and plots
##NCuniform_stem
###Individual models
# temperate_TMPavg_CI_one_NCuniform_stem

###Averaged model
coef_plot(temperate_TMPavg_average_model_full_NCuniform_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##NCuniform_crown
###Individual models
# temperate_TMPavg_CI_one_NCuniform_crown
###Averaged model
coef_plot(temperate_TMPavg_average_model_full_NCuniform_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_stem
###Individual models
# temperate_TMPavg_CI_one_FBD_stem
###Averaged model
coef_plot(temperate_TMPavg_average_model_full_FBD_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_crown
###Individual models
# temperate_TMPavg_CI_one_FBD_crown
# temperate_TMPavg_CI_three_FBD_crown

###Averaged model
coef_plot(temperate_TMPavg_average_model_full_FBD_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

## Both

### Alternative causal models
```{r Both - Define the potential causal models TMPavg, fig.width=10, fig.height=6}
both_TMPavg_models <- define_model_set(
  one = c(Poly_id ~ TMPavg, Poly_id ~ Colony_size),
  two = c(TMPavg ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ TMPavg, Poly_id ~ Colony_size),
  four = c(TMPavg ~ Colony_size, Poly_id ~ Colony_size)
)

#TMP model set - 4 models
plot_model_set(both_TMPavg_models, box_x = 22, box_y = 8, text_size = 3.5)

```

### Path analysis
```{r Both - Analyse models TMPavg, fig.width=24, fig.height=5}
#Run the models on each of the 4 different MCC trees
both_TMPavg_result_NCuniform_stem <- phylo_path(both_TMPavg_models, data = ant_data_both_TMPavg_selected_named, tree = both_anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
both_TMPavg_result_NCuniform_crown  <- phylo_path(both_TMPavg_models, data = ant_data_both_TMPavg_selected_named, tree = both_anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
both_TMPavg_result_FBD_stem <- phylo_path(both_TMPavg_models, data = ant_data_both_TMPavg_selected_named, tree = both_anttree_FBD_stem, model = "lambda", method = "logistic_MPLE")
both_TMPavg_result_FBD_crown <- phylo_path(both_TMPavg_models, data = ant_data_both_TMPavg_selected_named, tree = both_anttree_FBD_crown, model = "lambda", method = "logistic_MPLE")


#Summarise the models
both_TMPavg_result_NCuniform_stem_summary <- both_TMPavg_result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_TMPavg_result_NCuniform_stem_summary) <- NULL

both_TMPavg_result_NCuniform_crown_summary <- both_TMPavg_result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_TMPavg_result_NCuniform_crown_summary) <- NULL

both_TMPavg_result_FBD_stem_summary <- both_TMPavg_result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_TMPavg_result_FBD_stem_summary) <- NULL

both_TMPavg_result_FBD_crown_summary <- both_TMPavg_result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(both_TMPavg_result_FBD_crown_summary) <- NULL

#Produce tables for Rmarkdown
kable(both_TMPavg_result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position") #The kableExtra chunk of code holds the table in position so that it does not start floating around the document
kable(both_TMPavg_result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(both_TMPavg_result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(both_TMPavg_result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")

# #Plot model summaries
# plot(summary(both_TMPavg_result_NCuniform_stem))
# plot(summary(both_TMPavg_result_NCuniform_crown))
# plot(summary(both_TMPavg_result_FBD_stem))
# plot(summary(both_TMPavg_result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage
both_TMPavg_average_model_full_NCuniform_stem <- average(both_TMPavg_result_NCuniform_stem, avg_method = "full")
both_TMPavg_average_model_full_NCuniform_crown <- average(both_TMPavg_result_NCuniform_crown, avg_method = "full")
both_TMPavg_average_model_full_FBD_stem <- average(both_TMPavg_result_FBD_stem, avg_method = "full")
both_TMPavg_average_model_full_FBD_crown <- average(both_TMPavg_result_FBD_crown, avg_method = "full")

# TMPsd_average_model <- average(TMPsd_result, avg_method = 'conditional') #no 'shrinkage'
plot(both_TMPavg_average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(both_TMPavg_average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(both_TMPavg_average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(both_TMPavg_average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
```

#### Estimate confidence intervals for path coefficients
```{r Both - TMP path coefficients CI, fig.width=19, fig.height=2}
#Estimate confidence intervals for path coefficients
##NCuniform_stem
# both_TMPavg_CI_two_NCuniform_stem <- choice(both_TMPavg_result_NCuniform_stem, "two", boot = 500)
# both_TMPavg_CI_one_NCuniform_stem <- choice(both_TMPavg_result_NCuniform_stem, "one", boot = 500)
# 
# ##NCuniform_crown
# both_TMPavg_CI_two_NCuniform_crown <- choice(both_TMPavg_result_NCuniform_crown, "two", boot = 500)
# both_TMPavg_CI_one_NCuniform_crown <- choice(both_TMPavg_result_NCuniform_crown, "one", boot = 500)
# 
# ##FBD_stem
# both_TMPavg_CI_two_FBD_stem <- choice(both_TMPavg_result_FBD_stem, "two", boot = 500)
# both_TMPavg_CI_one_FBD_stem <- choice(both_TMPavg_result_FBD_stem, "one", boot = 500)
# 
# ##FBD_crown
# both_TMPavg_CI_two_FBD_crown <- choice(both_TMPavg_result_FBD_crown, "two", boot = 500)
# both_TMPavg_CI_one_FBD_crown <- choice(both_TMPavg_result_FBD_crown, "one", boot = 500)

#Print out the tables and plots
##NCuniform_stem
###Individual models
# both_TMPavg_CI_two_NCuniform_stem
# both_TMPavg_CI_one_NCuniform_stem

###Averaged model
coef_plot(both_TMPavg_average_model_full_NCuniform_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##NCuniform_crown
###Individual models
# both_TMPavg_CI_two_NCuniform_crown
# both_TMPavg_CI_one_NCuniform_crown
###Averaged model
coef_plot(both_TMPavg_average_model_full_NCuniform_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_stem
###Individual models
# both_TMPavg_CI_two_FBD_stem
# both_TMPavg_CI_one_FBD_stem
###Averaged model
coef_plot(both_TMPavg_average_model_full_FBD_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_crown
###Individual models
# both_TMPavg_CI_two_FBD_crown
# both_TMPavg_CI_one_FBD_crown
###Averaged model
coef_plot(both_TMPavg_average_model_full_FBD_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```