---
title: "Ant Climate Project"
subtitle: "Path analysis - TMPsd and PREavg in the same model"
author: "Louis Bell-Roberts"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
    includes:  
      in_header: preamble-latex.tex
urlcolor: blue
date: \today
---

\tableofcontents
\newpage 

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F, fig.align='center')
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = T)
# Packages
library(data.table)
library(knitr)
library(ape)
library(ggtree) ## Basic ggplot package for trees
library(ggtreeExtra) ## For fancy tree plotting
library(ufs) ## For ggqq plot
library(phylolm)
library(rr2)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(tibble)
library(phylopath)
library(phylolm)
library(phytools)
theme_set(theme_minimal())
library(kableExtra)
library(stringr)
# global plotting options for histogram
xmin= -7.5
xmax= 0
```

Read in the ant data and prepare the variables for path analysis. There are 474 species for which data is available for colony size and climatic variables, excluding special ants.
```{r Read in ant data}
ant_data <- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/New_transformations/AntClm_CSize_all_230710.csv") #After species with unusual biology removed = 474 species

#Assign rownames as species names
rownames(ant_data) <- ant_data$valid_species_name

#Log transform colony size variable
ant_data$colony.size.y <- log10(ant_data$colony.size.y)

#Square root transform PREavg_avg variable
ant_data$PREavg_avg <- sqrt(ant_data$PREavg_avg)

#Square root transform TMPsd_avg variable
ant_data$TMPsd_avg <- sqrt(ant_data$TMPsd_avg)

#Assign Poly_id as a factor
ant_data$poly_id <- as.factor(ant_data$poly_id)


#Read in trees
anttree_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_NCuniform_stem_MCC.tre")
anttree_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_NCuniform_crown_MCC.tre")
anttree_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_FBD_stem_MCC.tre")
anttree_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_FBD_crown_MCC.tre")

#Select columns of interest
ant_data_selected <- ant_data %>% dplyr::select(valid_species_name, poly_id, colony.size.y, TMPsd_avg, PREavg_avg)

#Rename the variables used in the analysis
ant_data_selected_named <- ant_data_selected %>% 
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         TMPsd=TMPsd_avg,
         PREavg=PREavg_avg)
```

# Create alternative causal models
We divide the path analysis into two analyses: (i) Analysis with only the temperature climatic variable (TMPsd) and (ii) Analysis with only the rainfall climatic variable (PREavg). This is because path analysis would not accept having more than one climatic predictor in the analysis because the linear models produced had highly significant relationships between the multiple climatic predictors being analysed. The potential model set is reduced to just two models for each analysis.

```{r Define the potential causal models TMPsd, fig.width=10, fig.height=6}
# ### The final set of path models ###
# #Define the models for the analysis: response before the ~, effector after the ~
models <- define_model_set(
  one = c(Poly_id ~ TMPsd, Poly_id ~ Colony_size),
  two = c(TMPsd ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ TMPsd, Poly_id ~ Colony_size),
  four = c(TMPsd ~ Colony_size, Poly_id ~ Colony_size),
  five = c(Poly_id ~ PREavg, Poly_id ~ Colony_size),
  six = c(PREavg ~ Poly_id, Poly_id ~ Colony_size),
  seven = c(Colony_size ~ PREavg, Poly_id ~ Colony_size),
  eight = c(PREavg ~ Colony_size, Poly_id ~ Colony_size)
)

plot_model_set(models, box_x = 22, box_y = 8, text_size = 3.5)
```

# Path analysis
```{r Analyse models TMPsd, fig.width=14, fig.height=6}
#Run the models on each of the 4 different MCC trees
result_NCuniform_stem <- phylo_path(models, data = ant_data_selected_named, tree = anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
result_NCuniform_crown <- phylo_path(models, data = ant_data_selected_named, tree = anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
result_FBD_stem <- phylo_path(models, data = ant_data_selected_named, tree = anttree_FBD_stem, model = "lambda", method = "logistic_MPLE")
result_FBD_crown <- phylo_path(models, data = ant_data_selected_named, tree = anttree_FBD_crown, model = "lambda", method = "logistic_MPLE")

#Summarise the models
result_NCuniform_stem_summary <- result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(result_NCuniform_stem_summary) <- NULL

result_NCuniform_crown_summary <- result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)  #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(result_NCuniform_crown_summary) <- NULL

result_FBD_stem_summary <- result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2) #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(result_FBD_stem_summary) <- NULL

result_FBD_crown_summary <- result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2) #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(result_FBD_crown_summary) <- NULL




#Produce tables for Rmarkdown
kable(result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position") #The kableExtra chunk of code holds the table in position so that it does not start floating around the document
kable(result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")


#Plot model summaries
# plot(summary(result_NCuniform_stem))
# plot(summary(result_NCuniform_crown))
# plot(summary(result_FBD_stem))
# plot(summary(result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage
average_model_full_NCuniform_stem <- average(result_NCuniform_stem, avg_method = "full")
average_model_full_NCuniform_crown <- average(result_NCuniform_crown, avg_method = "full")
average_model_full_FBD_stem <- average(result_FBD_stem, avg_method = "full")
average_model_full_FBD_crown <- average(result_FBD_crown, avg_method = "full")

#Plot
plot(average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
```


### Estimate confidence intervals for path coefficients
```{r Analyse models TMPsd - path coefficients CI, fig.width=3, fig.height=8}
# #Estimate confidence intervals for path coefficients
##NCuniform_stem
# CI_one_NCuniform_stem <- choice(result_NCuniform_stem, "one", boot = 500)
# CI_two_NCuniform_stem <- choice(result_NCuniform_stem, "two", boot = 500)
# 
# ##NCuniform_crown
# CI_one_NCuniform_crown <- choice(result_NCuniform_crown, "one", boot = 500)
# CI_two_NCuniform_crown <- choice(result_NCuniform_crown, "two", boot = 500)
# 
# ##FBD_stem
# CI_one_FBD_stem <- choice(result_FBD_stem, "one", boot = 500)
# CI_two_FBD_stem <- choice(result_FBD_stem, "two", boot = 500)
# 
# ##FBD_crown
# CI_one_FBD_crown <- choice(result_FBD_crown, "one", boot = 500)
# CI_two_FBD_crown <- choice(result_FBD_crown, "two", boot = 500)
# 
# #Print out the tables and plots
# ##NCuniform_stem
# ###Individual models
# CI_one_NCuniform_stem$lower
# CI_two_NCuniform_stem$coef
# ###Averaged model
# coef_plot(average_model_full_NCuniform_stem, error_bar = "ci", reverse_order = TRUE) +
#   ggplot2::coord_flip() +
#   ggplot2::theme_bw(base_size = 17)
# 
# ##NCuniform_crown
# ###Individual models
# CI_one_NCuniform_crown
# CI_two_NCuniform_crown
# ###Averaged model
# coef_plot(average_model_full_NCuniform_crown, error_bar = "ci", reverse_order = TRUE) + 
#   ggplot2::coord_flip() + 
#   ggplot2::theme_bw(base_size = 17)
# 
# ##FBD_stem
# ###Individual models
# CI_one_FBD_stem
# CI_two_FBD_stem
# ###Averaged model
# coef_plot(average_model_full_FBD_stem, error_bar = "ci", reverse_order = TRUE) + 
#   ggplot2::coord_flip() + 
#   ggplot2::theme_bw(base_size = 17)
# 
# ##FBD_crown
# ###Individual models
# CI_one_FBD_crown
# CI_two_FBD_crown
# ###Averaged model
# coef_plot(average_model_full_FBD_crown, error_bar = "ci", reverse_order = TRUE) + 
#   ggplot2::coord_flip() + 
#   ggplot2::theme_bw(base_size = 17)
```


