---
title: "Ant Climate Project"
subtitle: "Path analysis using PCA - Regional using conditional averaging"
author: "Louis Bell-Roberts"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
    includes:  
      in_header: preamble-latex.tex
urlcolor: blue
date: \today
---

\tableofcontents
\newpage 

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F, fig.align='center')
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = T)
# Packages
library(knitr)
library(ape)
library(ggtree) ## Basic ggplot package for trees
library(ggtreeExtra) ## For fancy tree plotting
library(ufs) ## For ggqq plot
library(phylolm)
library(rr2)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(phylopath)
library(phytools)
theme_set(theme_minimal())
library(kableExtra)
library(stringr)
library(grid)
library(gridExtra)
# global plotting options for histogram
xmin= -7.5
xmax= 0

##########################
#Load custom functions

#Function for extracting Path coefficient, SE, and 95% confidence interval from the Bootstrapped model results
generate_stats <- function(result, value, MCC) {
  CS_WP <- c(round(result$coef["Colony_size", "Poly_id"], 2), 
             round(result$se["Colony_size", "Poly_id"], 2), 
             round(result$lower["Colony_size", "Poly_id"], 2), 
             round(result$upper["Colony_size", "Poly_id"], 2))
  
  Climate_WP <- c(round(result$coef["Climate1", "Poly_id"], 2), 
                  round(result$se["Climate1", "Poly_id"], 2), 
                  round(result$lower["Climate1", "Poly_id"], 2), 
                  round(result$upper["Climate1", "Poly_id"], 2))
  
  WP_Climate <- c(round(result$coef["Poly_id", "Climate1"], 2), 
                  round(result$se["Poly_id", "Climate1"], 2), 
                  round(result$lower["Poly_id", "Climate1"], 2), 
                  round(result$upper["Poly_id", "Climate1"], 2))
  
  CS_Climate <- c(round(result$coef["Colony_size", "Climate1"], 2), 
                  round(result$se["Colony_size", "Climate1"], 2), 
                  round(result$lower["Colony_size", "Climate1"], 2), 
                  round(result$upper["Colony_size", "Climate1"], 2))
  
  Climate_CS <- c(round(result$coef["Climate1", "Colony_size"], 2), 
                  round(result$se["Climate1", "Colony_size"], 2), 
                  round(result$lower["Climate1", "Colony_size"], 2), 
                  round(result$upper["Climate1", "Colony_size"], 2))
  
  stats_noname <- as.data.frame(t(data.frame(CS_affects_WP = CS_WP, 
                                             Climate_affects_WP = Climate_WP, 
                                             WP_affects_Climate = WP_Climate, 
                                             CS_affects_Climate = CS_Climate,
                                             Climate_affects_CS = Climate_CS)))
  
  stats <- rename(stats_noname, 
                  Path_coefficient = V1, 
                  SE = V2, 
                  Lower_95_CI = V3, 
                  Upper_95_CI = V4)
  
  # Add the column "Model_number" to the first position
  stats <- mutate(stats, Model_number := value, Tree := MCC)
  
  # Add row names to a new column
  stats <- rownames_to_column(stats, var = "Causal_relationship")
  
  return(stats)
}


###############


#Function for extracting Path coefficient, SE, and 95% confidence interval from the averaged model results
generate_stats_avg_mods <- function(result, MCC) {
  CS_WP <- c(round(result$coef["Colony_size", "Poly_id"], 2), 
             round(result$se["Colony_size", "Poly_id"], 2), 
             round(result$lower["Colony_size", "Poly_id"], 2), 
             round(result$upper["Colony_size", "Poly_id"], 2))
  
  Climate_WP <- c(round(result$coef["Climate1", "Poly_id"], 2), 
             round(result$se["Climate1", "Poly_id"], 2), 
             round(result$lower["Climate1", "Poly_id"], 2), 
             round(result$upper["Climate1", "Poly_id"], 2))
  
  WP_Climate <- c(round(result$coef["Poly_id", "Climate1"], 2), 
             round(result$se["Poly_id", "Climate1"], 2), 
             round(result$lower["Poly_id", "Climate1"], 2), 
             round(result$upper["Poly_id", "Climate1"], 2))
  
  CS_Climate <- c(round(result$coef["Colony_size", "Climate1"], 2), 
             round(result$se["Colony_size", "Climate1"], 2), 
             round(result$lower["Colony_size", "Climate1"], 2), 
             round(result$upper["Colony_size", "Climate1"], 2))
  
  Climate_CS <- c(round(result$coef["Climate1", "Colony_size"], 2), 
             round(result$se["Climate1", "Colony_size"], 2), 
             round(result$lower["Climate1", "Colony_size"], 2), 
             round(result$upper["Climate1", "Colony_size"], 2))
    
  stats_noname <- as.data.frame(t(data.frame(CS_affects_WP = CS_WP, 
                                             Climate_affects_WP = Climate_WP, 
                                             WP_affects_Climate = WP_Climate, 
                                             CS_affects_Climate = CS_Climate,
                                             Climate_affects_CS = Climate_CS)))
  
  stats <- rename(stats_noname, 
                                 Path_coefficient = V1, 
                                 SE = V2, 
                                 Lower_95_CI = V3, 
                                 Upper_95_CI = V4)
  
  # Add the column "MCC" to the first position
  stats <- mutate(stats, Tree := MCC)
  
  # Add row names to a new column
  stats <- rownames_to_column(stats, var = "Causal_relationship")
  
  return(stats)
}


###############

#Function for creating model selection table and creating table with path coefficients, SE, and 95% confidence interval 
Create_coef_table <- function(result_NCuniform_stem, result_NCuniform_crown, result_FBD_stem, result_FBD_crown, filename_region) {

  ############ Create model selection table  ############ 
  
  #NCuniform_stem
  NCuniform_stem_summary <- result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
  #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
  rownames(NCuniform_stem_summary) <- NULL
  NCuniform_stem_summary <- NCuniform_stem_summary %>%
    mutate(phylogeny = "NC uniform stem") %>%
    select(phylogeny, everything())
  
  #NCuniform_crown
  NCuniform_crown_summary <- result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
  #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
  rownames(NCuniform_crown_summary) <- NULL
  NCuniform_crown_summary <- NCuniform_crown_summary %>%
    mutate(phylogeny = "NC uniform crown") %>%
    select(phylogeny, everything())
  
  #FBD_stem
  FBD_stem_summary <- result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
  #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
  rownames(FBD_stem_summary) <- NULL
  FBD_stem_summary <- FBD_stem_summary %>%
    mutate(phylogeny = "FBD stem") %>%
    select(phylogeny, everything())
  
  #FBD_crown
  FBD_crown_summary <- result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
  #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
  rownames(FBD_crown_summary) <- NULL
  FBD_crown_summary <- FBD_crown_summary %>%
    mutate(phylogeny = "FBD crown") %>%
    select(phylogeny, everything())
  
  ##Combine the four data frames
  combined_summaries <- rbind(NCuniform_stem_summary, NCuniform_crown_summary, FBD_stem_summary, FBD_crown_summary)
  write.csv(combined_summaries, file = paste0("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_", filename_region, "_summary_conditional_avg.csv"), row.names = FALSE)
  
  
  
  ############ Calculate confidence intervals and create table  ############ 
  
  #NCuniform_stem
  NCuniform_stem_result_one <- choice(result_NCuniform_stem, "one", boot = 500)
  NCuniform_stem_result_two <- choice(result_NCuniform_stem, "two", boot = 500)
  NCuniform_stem_result_three <- choice(result_NCuniform_stem, "three", boot = 500)
  NCuniform_stem_result_four <- choice(result_NCuniform_stem, "four", boot = 500)
  
  NCuniform_stem_coef_stats_one <- generate_stats(result = NCuniform_stem_result_one, value = "One", MCC = "NCuniform_stem")
  NCuniform_stem_coef_stats_two <- generate_stats(result = NCuniform_stem_result_two, value = "Two", MCC = "NCuniform_stem")
  NCuniform_stem_coef_stats_three <- generate_stats(result = NCuniform_stem_result_three, value = "Three", MCC = "NCuniform_stem")
  NCuniform_stem_coef_stats_four <- generate_stats(result = NCuniform_stem_result_four, value = "Four", MCC = "NCuniform_stem")
  NCuniform_stem_coef_stats_all_mod <- rbind(NCuniform_stem_coef_stats_one, NCuniform_stem_coef_stats_two, NCuniform_stem_coef_stats_three, NCuniform_stem_coef_stats_four)
  
  #NCuniform_crown
  NCuniform_crown_result_one <- choice(result_NCuniform_crown, "one", boot = 500)
  NCuniform_crown_result_two <- choice(result_NCuniform_crown, "two", boot = 500)
  NCuniform_crown_result_three <- choice(result_NCuniform_crown, "three", boot = 500)
  NCuniform_crown_result_four <- choice(result_NCuniform_crown, "four", boot = 500)
  
  NCuniform_crown_coef_stats_one <- generate_stats(result = NCuniform_crown_result_one, value = "One", MCC = "NCuniform_crown")
  NCuniform_crown_coef_stats_two <- generate_stats(result = NCuniform_crown_result_two, value = "Two", MCC = "NCuniform_crown")
  NCuniform_crown_coef_stats_three <- generate_stats(result = NCuniform_crown_result_three, value = "Three", MCC = "NCuniform_crown")
  NCuniform_crown_coef_stats_four <- generate_stats(result = NCuniform_crown_result_four, value = "Four", MCC = "NCuniform_crown")
  NCuniform_crown_coef_stats_all_mod <- rbind(NCuniform_crown_coef_stats_one, NCuniform_crown_coef_stats_two, NCuniform_crown_coef_stats_three, NCuniform_crown_coef_stats_four)
  
  #FBD_stem
  FBD_stem_result_one <- choice(result_FBD_stem, "one", boot = 500)
  FBD_stem_result_two <- choice(result_FBD_stem, "two", boot = 500)
  FBD_stem_result_three <- choice(result_FBD_stem, "three", boot = 500)
  FBD_stem_result_four <- choice(result_FBD_stem, "four", boot = 500)
  
  FBD_stem_coef_stats_one <- generate_stats(result = FBD_stem_result_one, value = "One", MCC = "FBD_stem")
  FBD_stem_coef_stats_two <- generate_stats(result = FBD_stem_result_two, value = "Two", MCC = "FBD_stem")
  FBD_stem_coef_stats_three <- generate_stats(result = FBD_stem_result_three, value = "Three", MCC = "FBD_stem")
  FBD_stem_coef_stats_four <- generate_stats(result = FBD_stem_result_four, value = "Four", MCC = "FBD_stem")
  FBD_stem_coef_stats_all_mod <- rbind(FBD_stem_coef_stats_one, FBD_stem_coef_stats_two, FBD_stem_coef_stats_three, FBD_stem_coef_stats_four)
  
  #FBD_crown
  FBD_crown_result_one <- choice(result_FBD_crown, "one", boot = 500)
  FBD_crown_result_two <- choice(result_FBD_crown, "two", boot = 500)
  FBD_crown_result_three <- choice(result_FBD_crown, "three", boot = 500)
  FBD_crown_result_four <- choice(result_FBD_crown, "four", boot = 500)
  
  FBD_crown_coef_stats_one <- generate_stats(result = FBD_crown_result_one, value = "One", MCC = "FBD_crown")
  FBD_crown_coef_stats_two <- generate_stats(result = FBD_crown_result_two, value = "Two", MCC = "FBD_crown")
  FBD_crown_coef_stats_three <- generate_stats(result = FBD_crown_result_three, value = "Three", MCC = "FBD_crown")
  FBD_crown_coef_stats_four <- generate_stats(result = FBD_crown_result_four, value = "Four", MCC = "FBD_crown")
  FBD_crown_coef_stats_all_mod <- rbind(FBD_crown_coef_stats_one, FBD_crown_coef_stats_two, FBD_crown_coef_stats_three, FBD_crown_coef_stats_four)
  
  PA_coef_stats <- rbind(NCuniform_stem_coef_stats_all_mod, NCuniform_crown_coef_stats_all_mod, FBD_stem_coef_stats_all_mod, FBD_crown_coef_stats_all_mod)
  write.csv(PA_coef_stats, file = paste0("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_", filename_region, "_coef_stats_conditional_avg.csv"), row.names = F)
  
}


###############

#Function for creating creating table with path coefficients, SE, and 95% confidence interval for the averaged models
Create_coef_table_averaged_model <- function(result_NCuniform_stem_average, result_NCuniform_crown_average, result_FBD_stem_average, result_FBD_crown_average, filename_region) {

  ############ Calculate confidence intervals and create table  ############ 
  
  #NCuniform_stem
  NCuniform_stem_coef_stats <- generate_stats_avg_mods(result = result_NCuniform_stem_average, MCC = "NCuniform_stem")

  #NCuniform_crown
  NCuniform_crown_coef_stats <- generate_stats_avg_mods(result = result_NCuniform_crown_average, MCC = "NCuniform_crown")

  #FBD_stem
  FBD_stem_coef_stats <- generate_stats_avg_mods(result = result_FBD_stem_average, MCC = "FBD_stem")

  #FBD_crown
  FBD_crown_coef_stats <- generate_stats_avg_mods(result = result_FBD_crown_average, MCC = "FBD_crown")
  
  PA_coef_stats <- rbind(NCuniform_stem_coef_stats, NCuniform_crown_coef_stats, FBD_stem_coef_stats, FBD_crown_coef_stats)
  write.csv(PA_coef_stats, file = paste0("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_", filename_region, "_coef_stats_conditional_averaged_model.csv"), row.names = F)
  
}

```


```{r Read in ant data}
#Tropical
ant_data_tropical_NCuniform_stem <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Tropical/NCuniform_stem_tropical_PCA_231117.csv") #NC_uniform_stem
ant_data_tropical_NCuniform_crown <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Tropical/NCuniform_crown_tropical_PCA_231117.csv") #NC_uniform_crown
ant_data_tropical_FBD_stem <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Tropical/FBD_stem_tropical_PCA_231117.csv") #FBD_stem
ant_data_tropical_FBD_crown <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Tropical/FBD_crown_tropical_PCA_231117.csv") #FBD_crown

#Temperate
ant_data_temperate_NCuniform_stem <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Temperate/NCuniform_stem_temperate_PCA_231117.csv") #NC_uniform_stem
ant_data_temperate_NCuniform_crown <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Temperate/NCuniform_crown_temperate_PCA_231117.csv") #NC_uniform_crown
ant_data_temperate_FBD_stem <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Temperate/FBD_stem_temperate_PCA_231117.csv") #FBD_stem
ant_data_temperate_FBD_crown <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Temperate/FBD_crown_temperate_PCA_231117.csv") #FBD_crown

#Both
ant_data_both_NCuniform_stem <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Both/NCuniform_stem_both_PCA_231117.csv") #NC_uniform_stem
ant_data_both_NCuniform_crown <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Both/NCuniform_crown_both_PCA_231117.csv") #NC_uniform_crown
ant_data_both_FBD_stem <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Both/FBD_stem_both_PCA_231117.csv") #FBD_stem
ant_data_both_FBD_crown <- read.csv(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/Tropical_vs_temperate/PCA_MCC_trees_data/Both/FBD_crown_both_PCA_231117.csv") #FBD_crown

##Assign rownames as species names
#Tropical
rownames(ant_data_tropical_NCuniform_stem) <- ant_data_tropical_NCuniform_stem$valid_species_name
rownames(ant_data_tropical_NCuniform_crown) <- ant_data_tropical_NCuniform_crown$valid_species_name
rownames(ant_data_tropical_FBD_stem) <- ant_data_tropical_FBD_stem$valid_species_name
rownames(ant_data_tropical_FBD_crown) <- ant_data_tropical_FBD_crown$valid_species_name

#Temperate
rownames(ant_data_temperate_NCuniform_stem) <- ant_data_temperate_NCuniform_stem$valid_species_name
rownames(ant_data_temperate_NCuniform_crown) <- ant_data_temperate_NCuniform_crown$valid_species_name
rownames(ant_data_temperate_FBD_stem) <- ant_data_temperate_FBD_stem$valid_species_name
rownames(ant_data_temperate_FBD_crown) <- ant_data_temperate_FBD_crown$valid_species_name

#Both
rownames(ant_data_both_NCuniform_stem) <- ant_data_both_NCuniform_stem$valid_species_name
rownames(ant_data_both_NCuniform_crown) <- ant_data_both_NCuniform_crown$valid_species_name
rownames(ant_data_both_FBD_stem) <- ant_data_both_FBD_stem$valid_species_name
rownames(ant_data_both_FBD_crown) <- ant_data_both_FBD_crown$valid_species_name

##Log transform colony size variable
#Tropical
ant_data_tropical_NCuniform_stem$colony.size.y <- log10(ant_data_tropical_NCuniform_stem$colony.size.y)
ant_data_tropical_NCuniform_crown$colony.size.y <- log10(ant_data_tropical_NCuniform_crown$colony.size.y)
ant_data_tropical_FBD_stem$colony.size.y <- log10(ant_data_tropical_FBD_stem$colony.size.y)
ant_data_tropical_FBD_crown$colony.size.y <- log10(ant_data_tropical_FBD_crown$colony.size.y)

#Temperate
ant_data_temperate_NCuniform_stem$colony.size.y <- log10(ant_data_temperate_NCuniform_stem$colony.size.y)
ant_data_temperate_NCuniform_crown$colony.size.y <- log10(ant_data_temperate_NCuniform_crown$colony.size.y)
ant_data_temperate_FBD_stem$colony.size.y <- log10(ant_data_temperate_FBD_stem$colony.size.y)
ant_data_temperate_FBD_crown$colony.size.y <- log10(ant_data_temperate_FBD_crown$colony.size.y)

#Both
ant_data_both_NCuniform_stem$colony.size.y <- log10(ant_data_both_NCuniform_stem$colony.size.y)
ant_data_both_NCuniform_crown$colony.size.y <- log10(ant_data_both_NCuniform_crown$colony.size.y)
ant_data_both_FBD_stem$colony.size.y <- log10(ant_data_both_FBD_stem$colony.size.y)
ant_data_both_FBD_crown$colony.size.y <- log10(ant_data_both_FBD_crown$colony.size.y)

##Assign Poly_id as a factor
#Tropical
ant_data_tropical_NCuniform_stem$poly_id <- as.factor(ant_data_tropical_NCuniform_stem$poly_id)
ant_data_tropical_NCuniform_crown$poly_id <- as.factor(ant_data_tropical_NCuniform_crown$poly_id)
ant_data_tropical_FBD_stem$poly_id <- as.factor(ant_data_tropical_FBD_stem$poly_id)
ant_data_tropical_FBD_crown$poly_id <- as.factor(ant_data_tropical_FBD_crown$poly_id)

#Temperate
ant_data_temperate_NCuniform_stem$poly_id <- as.factor(ant_data_temperate_NCuniform_stem$poly_id)
ant_data_temperate_NCuniform_crown$poly_id <- as.factor(ant_data_temperate_NCuniform_crown$poly_id)
ant_data_temperate_FBD_stem$poly_id <- as.factor(ant_data_temperate_FBD_stem$poly_id)
ant_data_temperate_FBD_crown$poly_id <- as.factor(ant_data_temperate_FBD_crown$poly_id)

#Both
ant_data_both_NCuniform_stem$poly_id <- as.factor(ant_data_both_NCuniform_stem$poly_id)
ant_data_both_NCuniform_crown$poly_id <- as.factor(ant_data_both_NCuniform_crown$poly_id)
ant_data_both_FBD_stem$poly_id <- as.factor(ant_data_both_FBD_stem$poly_id)
ant_data_both_FBD_crown$poly_id <- as.factor(ant_data_both_FBD_crown$poly_id)


##Read in trees
#Tropical
anttree_tropical_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_stem_tropical_pruned_MCC.tre")
anttree_tropical_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_crown_tropical_pruned_MCC.tre")
anttree_tropical_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_stem_tropical_pruned_MCC.tre")
anttree_tropical_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_crown_tropical_pruned_MCC.tre")
#Temperate
anttree_temperate_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_stem_temperate_pruned_MCC.tre")
anttree_temperate_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_crown_temperate_pruned_MCC.tre")
anttree_temperate_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_stem_temperate_pruned_MCC.tre")
anttree_temperate_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_crown_temperate_pruned_MCC.tre")

#Both
anttree_both_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_stem_both_pruned_MCC.tre")
anttree_both_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/NCuniform_crown_both_pruned_MCC.tre")
anttree_both_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_stem_both_pruned_MCC.tre")
anttree_both_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/Tropical_vs_temperate/MCC_trees/FBD_crown_both_pruned_MCC.tre")

##Select columns of interest and rename them
#Tropical
ant_data_tropical_NCuniform_stem_selected_named <- ant_data_tropical_NCuniform_stem %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_tropical_NCuniform_crown_selected_named <- ant_data_tropical_NCuniform_crown %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_tropical_FBD_stem_selected_named <- ant_data_tropical_FBD_stem %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_tropical_FBD_crown_selected_named <- ant_data_tropical_FBD_crown %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

#Temperate


ant_data_tropical_NCuniform_stem_selected <- ant_data_tropical_NCuniform_stem %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PC1)

#Temperate
ant_data_temperate_NCuniform_stem_selected_named <- ant_data_temperate_NCuniform_stem %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_temperate_NCuniform_crown_selected_named <- ant_data_temperate_NCuniform_crown %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_temperate_FBD_stem_selected_named <- ant_data_temperate_FBD_stem %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_temperate_FBD_crown_selected_named <- ant_data_temperate_FBD_crown %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )


#Both
ant_data_both_NCuniform_stem_selected_named <- ant_data_both_NCuniform_stem %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_both_NCuniform_crown_selected_named <- ant_data_both_NCuniform_crown %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_both_FBD_stem_selected_named <- ant_data_both_FBD_stem %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )

ant_data_both_FBD_crown_selected_named <- ant_data_both_FBD_crown %>%
  dplyr::select(valid_species_name, poly_id, colony.size.y, PC1) %>%
  rename(
    Colony_size = colony.size.y,
    Poly_id = poly_id,
    Climate1 = PC1
  )
```

# Initial comments

- Read in the ant data and prepare the variables for path analysis. There are 474 species for which data is available for colony size and climatic variables, excluding special ants. Process repeated on the 4 different PCA datasets created using the 4 different MCC trees.

- We use PCA for phylogenetic path analysis as path analysis with both temperature and rainfall variables in the same models were always rejected, unless causal paths were drawn between climatic variables. This is likely because of the correlation between climatic variables. Path analaysis with PCA allows us to analyse both temperature and rainfall in the same causal models.

- The potential model set is reduced to just four models for each analysis, assuming that colony size has a direct effect on the number of worker castes (Bell-Roberts et al., 2023).

# Summary
- Greater colony size favours both greater worker size variation and allows invasion into drier regions. Both path coefficients are significant.

# Create alternative causal models
```{r Define the potential causal models, fig.width=10, fig.height=6}
models <- define_model_set(
  one = c(Poly_id ~ Climate1, Poly_id ~ Colony_size),
  two = c(Climate1 ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ Climate1, Poly_id ~ Colony_size),
  four = c(Climate1 ~ Colony_size, Poly_id ~ Colony_size)
)

#PRE model set - 4 models
plot_model_set(models, box_x = 22, box_y = 8, text_size = 3.5)

```

# Path analysis
## Tropical
### NCuniform stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Tropical NCuniform stem, fig.width=7, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_tropical_NCuniform_stem_selected_named$Climate1 <- -ant_data_tropical_NCuniform_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_tropical_NCuniform_stem <- phylo_path(models, data = ant_data_tropical_NCuniform_stem_selected_named, tree = anttree_tropical_NCuniform_stem, model = "lambda", method = "logistic_MPLE", lower.bound = 0, upper.bound = 1)
# result_tropical_NCuniform_stem$warnings
plot(summary(result_tropical_NCuniform_stem))
result_tropical_NCuniform_stem_average_conditional <- average(result_tropical_NCuniform_stem, avg_method = "conditional")
(result_tropical_NCuniform_stem_plot <- plot(result_tropical_NCuniform_stem_average_conditional, algorithm = 'nicely', curvature = 0.1, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_tropical_NCuniform_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### NCuniform crown tree
Factor loading PC1: TMP: positive; PRE: positive
```{r Analyse models Tropical NCuniform crown, fig.width=7, fig.height=7}
#Run the models on each of the 4 different MCC trees
result_tropical_NCuniform_crown <- phylo_path(models, data = ant_data_tropical_NCuniform_crown_selected_named, tree = anttree_tropical_NCuniform_crown, model = "lambda", method = "logistic_MPLE", lower.bound = 0, upper.bound = 1)
# result_tropical_NCuniform_crown$warnings
plot(summary(result_tropical_NCuniform_crown))
result_tropical_NCuniform_crown_average_conditional <- average(result_tropical_NCuniform_crown, avg_method = "conditional")
(result_tropical_NCuniform_crown_plot <- plot(result_tropical_NCuniform_crown_average_conditional, algorithm = 'nicely', curvature = 0.1, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_tropical_NCuniform_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### FBD stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Tropical FBD stem, fig.width=8, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_tropical_FBD_stem_selected_named$Climate1 <- -ant_data_tropical_FBD_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_tropical_FBD_stem <- phylo_path(models, data = ant_data_tropical_FBD_stem_selected_named, tree = anttree_tropical_FBD_stem, model = "lambda", method = "logistic_MPLE", lower.bound = 0, upper.bound = 1)
# result_tropical_FBD_stem$warnings
plot(summary(result_tropical_FBD_stem))
result_tropical_FBD_stem_average_conditional <- average(result_tropical_FBD_stem, avg_method = "conditional")
(result_tropical_FBD_stem_plot <- plot(result_tropical_FBD_stem_average_conditional, algorithm = 'nicely', curvature = 0.1, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_tropical_FBD_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```
### FBD crown tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Tropical FBD crown, fig.width=11, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_tropical_FBD_crown_selected_named$Climate1 <- -ant_data_tropical_FBD_crown_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_tropical_FBD_crown <- phylo_path(models, data = ant_data_tropical_FBD_crown_selected_named, tree = anttree_tropical_FBD_crown, model = "lambda", method = "logistic_MPLE", lower.bound = 0, upper.bound = 1)
# result_tropical_FBD_crown$warnings
plot(summary(result_tropical_FBD_crown))
result_tropical_FBD_crown_average_conditional <- average(result_tropical_FBD_crown, avg_method = "conditional")
(result_tropical_FBD_crown_plot <- plot(result_tropical_FBD_crown_average_conditional, algorithm = 'nicely', curvature = 0.1, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_tropical_FBD_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

## Temperate
### NCuniform stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Temperate NCuniform stem, fig.width=11, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_temperate_NCuniform_stem_selected_named$Climate1 <- -ant_data_temperate_NCuniform_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_temperate_NCuniform_stem <- phylo_path(models, data = ant_data_temperate_NCuniform_stem_selected_named, tree = anttree_temperate_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
# result_temperate_NCuniform_stem$warnings
plot(summary(result_temperate_NCuniform_stem))
result_temperate_NCuniform_stem_average_conditional <- average(result_temperate_NCuniform_stem, avg_method = "conditional")
(result_temperate_NCuniform_stem_plot <- plot(result_temperate_NCuniform_stem_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_temperate_NCuniform_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### NCuniform crown tree
Factor loading PC1: TMP: positive; PRE: positive
```{r Analyse models Temperate NCuniform crown, fig.width=10, fig.height=4}
#Run the models on each of the 4 different MCC trees
result_temperate_NCuniform_crown <- phylo_path(models, data = ant_data_temperate_NCuniform_crown_selected_named, tree = anttree_temperate_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
# result_temperate_NCuniform_crown$warnings
plot(summary(result_temperate_NCuniform_crown))
result_temperate_NCuniform_crown_average_conditional <- average(result_temperate_NCuniform_crown, avg_method = "conditional")
(result_temperate_NCuniform_crown_plot <- plot(result_temperate_NCuniform_crown_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_temperate_NCuniform_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### FBD stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Temperate FBD stem, fig.width=11, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_temperate_FBD_stem_selected_named$Climate1 <- -ant_data_temperate_FBD_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_temperate_FBD_stem <- phylo_path(models, data = ant_data_temperate_FBD_stem_selected_named, tree = anttree_temperate_FBD_stem, model = "lambda", method = "logistic_MPLE")
# result_temperate_FBD_stem$warnings
plot(summary(result_temperate_FBD_stem))
result_temperate_FBD_stem_average_conditional <- average(result_temperate_FBD_stem, avg_method = "conditional")
(result_temperate_FBD_stem_plot <- plot(result_temperate_FBD_stem_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_temperate_FBD_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### FBD crown tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Temperate FBD crown, fig.width=7, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_temperate_FBD_crown_selected_named$Climate1 <- -ant_data_temperate_FBD_crown_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_temperate_FBD_crown <- phylo_path(models, data = ant_data_temperate_FBD_crown_selected_named, tree = anttree_temperate_FBD_crown, model = "lambda", method = "logistic_MPLE")
# result_temperate_FBD_crown$warnings
plot(summary(result_temperate_FBD_crown))
result_temperate_FBD_crown_average_conditional <- average(result_temperate_FBD_crown, avg_method = "conditional")
(result_temperate_FBD_crown_plot <- plot(result_temperate_FBD_crown_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_temperate_FBD_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

## Both
### NCuniform stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Both NCuniform stem, fig.width=7, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_both_NCuniform_stem_selected_named$Climate1 <- -ant_data_both_NCuniform_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_both_NCuniform_stem <- phylo_path(models, data = ant_data_both_NCuniform_stem_selected_named, tree = anttree_both_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
# result_both_NCuniform_stem$warnings
plot(summary(result_both_NCuniform_stem))
result_both_NCuniform_stem_average_conditional <- average(result_both_NCuniform_stem, avg_method = "conditional")
(result_both_NCuniform_stem_plot <- plot(result_both_NCuniform_stem_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_both_NCuniform_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### NCuniform crown tree
Factor loading PC1: TMP: positive; PRE: positive
```{r Analyse models Both NCuniform crown, fig.width=7, fig.height=7}
#Run the models on each of the 4 different MCC trees
result_both_NCuniform_crown <- phylo_path(models, data = ant_data_both_NCuniform_crown_selected_named, tree = anttree_both_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
# result_both_NCuniform_crown$warnings
plot(summary(result_both_NCuniform_crown))
result_both_NCuniform_crown_average_conditional <- average(result_both_NCuniform_crown, avg_method = "conditional")
(result_both_NCuniform_crown_plot <- plot(result_both_NCuniform_crown_average_conditional, algorithm = 'nicely', curvature = 0.1, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_both_NCuniform_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### FBD stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Both FBD stem, fig.width=7, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_both_FBD_stem_selected_named$Climate1 <- -ant_data_both_FBD_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_both_FBD_stem <- phylo_path(models, data = ant_data_both_FBD_stem_selected_named, tree = anttree_both_FBD_stem, model = "lambda", method = "logistic_MPLE")
# result_both_FBD_stem$warnings
plot(summary(result_both_FBD_stem))
result_both_FBD_stem_average_conditional <- average(result_both_FBD_stem, avg_method = "conditional")
(result_both_FBD_stem_plot <- plot(result_both_FBD_stem_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_both_FBD_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

### FBD crown tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models Both FBD crown, fig.width=7, fig.height=4}
#Run the models on each of the 4 different MCC trees
ant_data_both_FBD_crown_selected_named$Climate1 <- -ant_data_both_FBD_crown_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_both_FBD_crown <- phylo_path(models, data = ant_data_both_FBD_crown_selected_named, tree = anttree_both_FBD_crown, model = "lambda", method = "logistic_MPLE")
# result_both_FBD_crown$warnings
plot(summary(result_both_FBD_crown))
result_both_FBD_crown_average_conditional <- average(result_both_FBD_crown, avg_method = "conditional")
(result_both_FBD_crown_plot <- plot(result_both_FBD_crown_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_both_FBD_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```
# Panel plots
```{r Panel plots - tropical, fig.width=22, fig.height=8}
# Create a PDF file
pdf("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Wordfiles/Paper drafting/AntEnv/Supplementary_materials/Figures/Path_analysis_tropical_PCA_average_4panel_conditional_avg.pdf", width = 11, height = 22)

#Make multipanel plot
Path_analysis_tropical_PCA_average_4panel.pdf <- grid.arrange(result_tropical_NCuniform_stem_plot, result_tropical_NCuniform_crown_plot, result_tropical_FBD_stem_plot, result_tropical_FBD_crown_plot, ncol = 1)

# Add labels to each panel
grid.text("a", x = 0.01, y = 0.96, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_tropical_PCA_average_4panel.pdf$layout$layout[1, 1]$panel_params)
grid.text("b", x = 0.01, y = 0.71, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_tropical_PCA_average_4panel.pdf$layout$layout[1, 2]$panel_params)
grid.text("c", x = 0.01, y = 0.46, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_tropical_PCA_average_4panel.pdf$layout$layout[2, 1]$panel_params)
grid.text("d", x = 0.01, y = 0.21, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_tropical_PCA_average_4panel.pdf$layout$layout[2, 2]$panel_params)

dev.off()

plot(Path_analysis_tropical_PCA_average_4panel.pdf)
```

```{r Panel plots - temperate, fig.width=22, fig.height=8}
# Create a PDF file
pdf("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Wordfiles/Paper drafting/AntEnv/Supplementary_materials/Figures/Path_analysis_temperate_PCA_average_4panel_conditional_avg.pdf", width = 11, height = 13)

#Make multipanel plot
Path_analysis_temperate_PCA_average_4panel.pdf <- grid.arrange(result_temperate_NCuniform_stem_plot, result_temperate_NCuniform_crown_plot, result_temperate_FBD_stem_plot, result_temperate_FBD_crown_plot, ncol = 1)

# Add labels to each panel
grid.text("a", x = 0.01, y = 0.96, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_temperate_PCA_average_4panel.pdf$layout$layout[1, 1]$panel_params)
grid.text("b", x = 0.01, y = 0.71, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_temperate_PCA_average_4panel.pdf$layout$layout[1, 2]$panel_params)
grid.text("c", x = 0.01, y = 0.46, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_temperate_PCA_average_4panel.pdf$layout$layout[2, 1]$panel_params)
grid.text("d", x = 0.01, y = 0.21, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_temperate_PCA_average_4panel.pdf$layout$layout[2, 2]$panel_params)

dev.off()

plot(Path_analysis_temperate_PCA_average_4panel.pdf)
```

```{r Panel plots - both, fig.width=22, fig.height=8}
# Create a PDF file
pdf("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Wordfiles/Paper drafting/AntEnv/Supplementary_materials/Figures/Path_analysis_both_PCA_average_4panel_conditional_avg.pdf", width = 11, height = 13)

#Make multipanel plot
Path_analysis_both_PCA_average_4panel.pdf <- grid.arrange(result_both_NCuniform_stem_plot, result_both_NCuniform_crown_plot, result_both_FBD_stem_plot, result_both_FBD_crown_plot, ncol = 1)

# Add labels to each panel
grid.text("a", x = 0.01, y = 0.96, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_both_PCA_average_4panel.pdf$layout$layout[1, 1]$panel_params)
grid.text("b", x = 0.01, y = 0.71, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_both_PCA_average_4panel.pdf$layout$layout[1, 2]$panel_params)
grid.text("c", x = 0.01, y = 0.46, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_both_PCA_average_4panel.pdf$layout$layout[2, 1]$panel_params)
grid.text("d", x = 0.01, y = 0.21, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_both_PCA_average_4panel.pdf$layout$layout[2, 2]$panel_params)

dev.off()

plot(Path_analysis_both_PCA_average_4panel.pdf)
```


```{r Summarise tropical model coefficients}
# Create_coef_table(result_NCuniform_stem = result_tropical_NCuniform_stem, result_NCuniform_crown = result_tropical_NCuniform_crown, result_FBD_stem = result_tropical_FBD_stem, result_FBD_crown = result_tropical_FBD_crown, filename_region = "Tropical")

Create_coef_table_averaged_model(result_NCuniform_stem_average = result_tropical_NCuniform_stem_average_conditional, result_NCuniform_crown_average = result_tropical_NCuniform_crown_average_conditional, result_FBD_stem_average = result_tropical_FBD_stem_average_conditional, result_FBD_crown_average = result_tropical_FBD_crown_average_conditional, filename_region = "Tropical")

```

```{r Summarise temperate model coefficients}
# Create_coef_table(result_NCuniform_stem = result_temperate_NCuniform_stem, result_NCuniform_crown = result_temperate_NCuniform_crown, result_FBD_stem = result_temperate_FBD_stem, result_FBD_crown = result_temperate_FBD_crown, filename_region = "Temperate")

Create_coef_table_averaged_model(result_NCuniform_stem_average = result_temperate_NCuniform_stem_average_conditional, result_NCuniform_crown_average = result_temperate_NCuniform_crown_average_conditional, result_FBD_stem_average = result_temperate_FBD_stem_average_conditional, result_FBD_crown_average = result_temperate_FBD_crown_average_conditional, filename_region = "Temperate")
```

```{r Summarise both model coefficients}

# Create_coef_table(result_NCuniform_stem = result_both_NCuniform_stem, result_NCuniform_crown = result_both_NCuniform_crown, result_FBD_stem = result_both_FBD_stem, result_FBD_crown = result_both_FBD_crown, filename_region = "Both")

Create_coef_table_averaged_model(result_NCuniform_stem_average = result_both_NCuniform_stem_average_conditional, result_NCuniform_crown_average = result_both_NCuniform_crown_average_conditional, result_FBD_stem_average = result_both_FBD_stem_average_conditional, result_FBD_crown_average = result_both_FBD_crown_average_conditional, filename_region = "Both")

```

```{r Combining tables}

#Combine the model selection tables
# combined_avg_mod_sel_tables <- rbind(read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/All_sp_474/Without_transformation/Phylo_PCA/Results/Path_analysis_Global_summary_conditional_avg.csv"), read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_Tropical_summary_conditional_avg.csv"), read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_Temperate_summary_conditional_avg.csv"), read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_Both_summary_conditional_avg.csv"))
# 
# climate_types_mod_sel <- c(rep("Global", 16), rep("Tropical", 16), rep("Temperate", 16), rep("Both", 16))
# 
# combined_avg_mod_mod_sel_tables_region <- cbind(combined_avg_mod_sel_tables, Region = climate_types_mod_sel)
# write.csv(combined_avg_mod_mod_sel_tables_region, file = "/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_All_Regions_model_selection_conditional_averaged_model.csv", row.names = F)

#combine the averaged model path coefficient tables and save
# combined_avg_mod_path_coef_tables <- rbind(read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/All_sp_474/Without_transformation/Phylo_PCA/Results/Path_analysis_Global_coef_stats_conditional_avged_models.csv"), read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_Tropical_coef_stats_conditional_averaged_model.csv"), read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_Temperate_coef_stats_conditional_averaged_model.csv"), read.csv("/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_Both_coef_stats_conditional_averaged_model.csv"))
# 
# climate_types_coef <- c(rep("Global", 20), rep("Tropical", 20), rep("Temperate", 20), rep("Both", 20))
# 
# combined_avg_mod_path_coef_tables_region <- cbind(combined_avg_mod_path_coef_tables, Region = climate_types_coef)
# write.csv(combined_avg_mod_path_coef_tables_region, file = "/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/Tropical_vs_Temperate_vs_Both/Without_transformation/Phylo_PCA/Results/Path_analysis_All_Regions_coef_stats_conditional_averaged_model.csv", row.names = F)
```