---
title: "Ant Climate Project"
subtitle: "Path analysis using PCA - Global using conditional averaging"
author: "Louis Bell-Roberts"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
    includes:  
      in_header: preamble-latex.tex
urlcolor: blue
date: \today
---

\tableofcontents
\newpage 

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F, fig.align='center')
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = T)
# Packages
library(knitr)
library(ape)
library(ggtree) ## Basic ggplot package for trees
library(ggtreeExtra) ## For fancy tree plotting
library(ufs) ## For ggqq plot
library(phylolm)
library(rr2)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(phylopath)
library(phytools)
theme_set(theme_minimal())
library(kableExtra)
library(stringr)
library(grid)
library(gridExtra)
# global plotting options for histogram
xmin= -7.5
xmax= 0
```


```{r Read in ant data}
ant_data_NCuniform_stem <- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/New_transformations/PCA_MCC_trees_data/NCuniform_stem_all_PCA_231116.csv") #474 species
ant_data_NCuniform_crown <- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/New_transformations/PCA_MCC_trees_data/NCuniform_crown_all_PCA_231116.csv")
ant_data_FBD_stem <- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/New_transformations/PCA_MCC_trees_data/FBD_stem_all_PCA_231116.csv")
ant_data_FBD_crown <- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/New_transformations/PCA_MCC_trees_data/FBD_crown_all_PCA_231116.csv")

#Assign rownames as species names
rownames(ant_data_NCuniform_stem) <- ant_data_NCuniform_stem$valid_species_name
rownames(ant_data_NCuniform_crown) <- ant_data_NCuniform_crown$valid_species_name
rownames(ant_data_FBD_stem) <- ant_data_FBD_stem$valid_species_name
rownames(ant_data_FBD_crown) <- ant_data_FBD_crown$valid_species_name

#Log transform colony size variable
ant_data_NCuniform_stem$colony.size.y <- log10(ant_data_NCuniform_stem$colony.size.y)
ant_data_NCuniform_crown$colony.size.y <- log10(ant_data_NCuniform_crown$colony.size.y)
ant_data_FBD_stem$colony.size.y <- log10(ant_data_FBD_stem$colony.size.y)
ant_data_FBD_crown$colony.size.y <- log10(ant_data_FBD_crown$colony.size.y)

#Assign Poly_id as a factor
ant_data_NCuniform_stem$poly_id <- as.factor(ant_data_NCuniform_stem$poly_id)
ant_data_NCuniform_crown$poly_id <- as.factor(ant_data_NCuniform_crown$poly_id)
ant_data_FBD_stem$poly_id <- as.factor(ant_data_FBD_stem$poly_id)
ant_data_FBD_crown$poly_id <- as.factor(ant_data_FBD_crown$poly_id)


#Read in trees
anttree_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_NCuniform_stem_MCC.tre")
anttree_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_NCuniform_crown_MCC.tre")
anttree_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_FBD_stem_MCC.tre")
anttree_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_FBD_crown_MCC.tre")

#Select columns of interest
anttree_NCuniform_stem_selected <- ant_data_NCuniform_stem %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PC1, PC2)
anttree_NCuniform_crown_selected <- ant_data_NCuniform_crown %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PC1, PC2)
anttree_FBD_stem_selected <- ant_data_FBD_stem %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PC1, PC2)
anttree_FBD_crown_selected <- ant_data_FBD_crown %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PC1, PC2)


#Rename the variables used in the analysis
anttree_NCuniform_stem_selected_named <- anttree_NCuniform_stem_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         Climate1=PC1,
         Climate2=PC2)

anttree_NCuniform_crown_selected_named <- anttree_NCuniform_crown_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         Climate1=PC1,
         Climate2=PC2)

anttree_FBD_stem_selected_named <- anttree_FBD_stem_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         Climate1=PC1,
         Climate2=PC2)

anttree_FBD_crown_selected_named <- anttree_FBD_crown_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         Climate1=PC1,
         Climate2=PC2)

```

# Initial comments

- Read in the ant data and prepare the variables for path analysis. There are 474 species for which data is available for colony size and climatic variables, excluding special ants. Process repeated on the 4 different PCA datasets created using the 4 different MCC trees.

- We use PCA for phylogenetic path analysis as path analysis with both temperature and rainfall variables in the same models were always rejected, unless causal paths were drawn between climatic variables. This is likely because of the correlation between climatic variables. Path analaysis with PCA allows us to analyse both temperature and rainfall in the same causal models.

- The potential model set is reduced to just four models for each analysis, assuming that colony size has a direct effect on the number of worker castes (Bell-Roberts et al., 2023).

# Summary
- Model 3 (climate affects colony size) most often comes out as the best model across trees. But there is no real pattern of any strong effect of climate and social complexity. Results also quite sensitive to phylogenetic uncertainty.

# Create alternative causal models
```{r Define the potential causal models, fig.width=10, fig.height=6}
models <- define_model_set(
  one = c(Poly_id ~ Climate1, Poly_id ~ Colony_size),
  two = c(Climate1 ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ Climate1, Poly_id ~ Colony_size),
  four = c(Climate1 ~ Colony_size, Poly_id ~ Colony_size)
)

#PRE model set - 4 models
(potential_causal_models <- plot_model_set(models, box_x = 22, box_y = 8, text_size = 3.5))
# ggsave(plot = potential_causal_models, filename = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Wordfiles/Paper drafting/AntEnv/Supplementary_materials/Figures/Potential_causal_models.pdf")

```

# Path analysis
## NCuniform stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models NCuniform stem, fig.width=7, fig.height=4}
#Run the models on each of the 4 different MCC trees
anttree_NCuniform_stem_selected_named$Climate1 <- -anttree_NCuniform_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_NCuniform_stem <- phylo_path(models, data = anttree_NCuniform_stem_selected_named, tree = anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE")
# result_NCuniform_stem$warnings
plot(summary(result_NCuniform_stem))
result_NCuniform_stem_average_conditional <- average(result_NCuniform_stem, avg_method = "conditional")
(result_NCuniform_stem_average_conditional_plot <- plot(result_NCuniform_stem_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_NCuniform_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

## NCuniform crown tree
Factor loading PC1: TMP: positive; PRE: positive
```{r Analyse models NCuniform crown, fig.width=7, fig.height=4}
#Run the models on each of the 4 different MCC trees
result_NCuniform_crown <- phylo_path(models, data = anttree_NCuniform_crown_selected_named, tree = anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE")
# result_NCuniform_crown$warnings
plot(summary(result_NCuniform_crown))
result_NCuniform_crown_average_conditional <- average(result_NCuniform_crown, avg_method = "conditional")
(result_NCuniform_crown_average_conditional_plot <- plot(result_NCuniform_crown_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_NCuniform_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

## FBD stem tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models FBD stem, fig.width=8, fig.height=4}
#Run the models on each of the 4 different MCC trees
anttree_FBD_stem_selected_named$Climate1 <- -anttree_FBD_stem_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_FBD_stem <- phylo_path(models, data = anttree_FBD_stem_selected_named, tree = anttree_FBD_stem, model = "lambda", method = "logistic_MPLE")
# result_FBD_stem$warnings
plot(summary(result_FBD_stem))
result_FBD_stem_average_conditional <- average(result_FBD_stem, avg_method = "conditional")
(result_FBD_stem_average_conditional_plot <- plot(result_FBD_stem_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_FBD_stem_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```
## FBD crown tree
Factor loading PC1: TMP: negative; PRE: negative
```{r Analyse models FBD crown, fig.width=11, fig.height=4}
#Run the models on each of the 4 different MCC trees
anttree_FBD_crown_selected_named$Climate1 <- -anttree_FBD_crown_selected_named$Climate1 #Reverse sign for each of the relationships with Climate
result_FBD_crown <- phylo_path(models, data = anttree_FBD_crown_selected_named, tree = anttree_FBD_crown, model = "lambda", method = "logistic_MPLE")
# result_FBD_crown$warnings
plot(summary(result_FBD_crown))
result_FBD_crown_average_conditional <- average(result_FBD_crown, avg_method = "conditional")
(result_FBD_crown_average_conditional_plot <- plot(result_FBD_crown_average_conditional, algorithm = 'sugiyama', curvature = 0.04, box_x = 20, box_y = 12, text_size = 5, labels = c(Colony_size = "CS",  Poly_id = "WP", Climate1 = "PC1"))
)

#CI
coef_plot(result_FBD_crown_average_conditional, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```
# Panel plots
```{r Panel plots, fig.width=22, fig.height=8}
# Create a PDF file
pdf("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Wordfiles/Paper drafting/AntEnv/Supplementary_materials/Figures/Path_analysis_global_PCA_average_4panel_conditional_avg.pdf", width = 11, height = 13)

#Make multipanel plot
Path_analysis_global_PCA_average_4panel.pdf <- grid.arrange(result_NCuniform_stem_average_conditional_plot, result_NCuniform_crown_average_conditional_plot, result_FBD_stem_average_conditional_plot, result_FBD_crown_average_conditional_plot, ncol = 1)

# Add labels to each panel
grid.text("a", x = 0.01, y = 0.96, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_global_PCA_average_4panel.pdf$layout$layout[1, 1]$panel_params)
grid.text("b", x = 0.01, y = 0.71, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_global_PCA_average_4panel.pdf$layout$layout[1, 2]$panel_params)
grid.text("c", x = 0.01, y = 0.46, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_global_PCA_average_4panel.pdf$layout$layout[2, 1]$panel_params)
grid.text("d", x = 0.01, y = 0.21, just = "left", gp = gpar(fontsize = 16, fontface = "bold"), vp = Path_analysis_global_PCA_average_4panel.pdf$layout$layout[2, 2]$panel_params)

dev.off()

plot(Path_analysis_global_PCA_average_4panel.pdf)
```


```{r Summarise the models}

#NCuniform_stem
NCuniform_stem_summary <- result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
#k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(NCuniform_stem_summary) <- NULL
NCuniform_stem_summary <- NCuniform_stem_summary %>%
  mutate(phylogeny = "NC uniform stem") %>%
  select(phylogeny, everything())

#NCuniform_crown
NCuniform_crown_summary <- result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
#k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(NCuniform_crown_summary) <- NULL
NCuniform_crown_summary <- NCuniform_crown_summary %>%
  mutate(phylogeny = "NC uniform crown") %>%
  select(phylogeny, everything())

#FBD_stem
FBD_stem_summary <- result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
#k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(FBD_stem_summary) <- NULL
FBD_stem_summary <- FBD_stem_summary %>%
  mutate(phylogeny = "FBD stem") %>%
  select(phylogeny, everything())

#FBD_crown
FBD_crown_summary <- result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc)
#k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(FBD_crown_summary) <- NULL
FBD_crown_summary <- FBD_crown_summary %>%
  mutate(phylogeny = "FBD crown") %>%
  select(phylogeny, everything())

##Combine the four data frames
combined_summaries <- rbind(NCuniform_stem_summary, NCuniform_crown_summary, FBD_stem_summary, FBD_crown_summary)
write.csv(combined_summaries, file = "/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/All_sp_474/Without_transformation/Phylo_PCA/Results/Path_analysis_Global_summary_conditional_avg.csv", row.names = FALSE)


######################################################################
#Function for extracting Path coefficient, SE, and 95% confidence interval from the Bootstrapped model results
generate_stats <- function(result, value, MCC) {
  CS_WP <- c(round(result$coef["Colony_size", "Poly_id"], 2), 
             round(result$se["Colony_size", "Poly_id"], 2), 
             round(result$lower["Colony_size", "Poly_id"], 2), 
             round(result$upper["Colony_size", "Poly_id"], 2))
  
  Climate_WP <- c(round(result$coef["Climate1", "Poly_id"], 2), 
             round(result$se["Climate1", "Poly_id"], 2), 
             round(result$lower["Climate1", "Poly_id"], 2), 
             round(result$upper["Climate1", "Poly_id"], 2))
  
  WP_Climate <- c(round(result$coef["Poly_id", "Climate1"], 2), 
             round(result$se["Poly_id", "Climate1"], 2), 
             round(result$lower["Poly_id", "Climate1"], 2), 
             round(result$upper["Poly_id", "Climate1"], 2))
  
  CS_Climate <- c(round(result$coef["Colony_size", "Climate1"], 2), 
             round(result$se["Colony_size", "Climate1"], 2), 
             round(result$lower["Colony_size", "Climate1"], 2), 
             round(result$upper["Colony_size", "Climate1"], 2))
  
  Climate_CS <- c(round(result$coef["Climate1", "Colony_size"], 2), 
             round(result$se["Climate1", "Colony_size"], 2), 
             round(result$lower["Climate1", "Colony_size"], 2), 
             round(result$upper["Climate1", "Colony_size"], 2))
    
  stats_noname <- as.data.frame(t(data.frame(CS_affects_WP = CS_WP, 
                                             Climate_affects_WP = Climate_WP, 
                                             WP_affects_Climate = WP_Climate, 
                                             CS_affects_Climate = CS_Climate,
                                             Climate_affects_CS = Climate_CS)))
  
  stats <- rename(stats_noname, 
                                 Path_coefficient = V1, 
                                 SE = V2, 
                                 Lower_95_CI = V3, 
                                 Upper_95_CI = V4)
  
  # Add the column "Model_number" to the first position
  stats <- mutate(stats, Model_number := value, Tree := MCC)
  
  # Add row names to a new column
  stats <- rownames_to_column(stats, var = "Causal_relationship")
  
  return(stats)
}

### Calculate confidence intervals ###
#NCuniform_stem
NCuniform_stem_result_one <- choice(result_NCuniform_stem, "one", boot = 500)
NCuniform_stem_result_two <- choice(result_NCuniform_stem, "two", boot = 500)
NCuniform_stem_result_three <- choice(result_NCuniform_stem, "three", boot = 500)
NCuniform_stem_result_four <- choice(result_NCuniform_stem, "four", boot = 500)

NCuniform_stem_coef_stats_one <- generate_stats(result = NCuniform_stem_result_one, value = "One", MCC = "NCuniform_stem")
NCuniform_stem_coef_stats_two <- generate_stats(result = NCuniform_stem_result_two, value = "Two", MCC = "NCuniform_stem")
NCuniform_stem_coef_stats_three <- generate_stats(result = NCuniform_stem_result_three, value = "Three", MCC = "NCuniform_stem")
NCuniform_stem_coef_stats_four <- generate_stats(result = NCuniform_stem_result_four, value = "Four", MCC = "NCuniform_stem")
NCuniform_stem_coef_stats_all_mod <- rbind(NCuniform_stem_coef_stats_one, NCuniform_stem_coef_stats_two, NCuniform_stem_coef_stats_three, NCuniform_stem_coef_stats_four)

#NCuniform_crown
NCuniform_crown_result_one <- choice(result_NCuniform_crown, "one", boot = 500)
NCuniform_crown_result_two <- choice(result_NCuniform_crown, "two", boot = 500)
NCuniform_crown_result_three <- choice(result_NCuniform_crown, "three", boot = 500)
NCuniform_crown_result_four <- choice(result_NCuniform_crown, "four", boot = 500)

NCuniform_crown_coef_stats_one <- generate_stats(result = NCuniform_crown_result_one, value = "One", MCC = "NCuniform_crown")
NCuniform_crown_coef_stats_two <- generate_stats(result = NCuniform_crown_result_two, value = "Two", MCC = "NCuniform_crown")
NCuniform_crown_coef_stats_three <- generate_stats(result = NCuniform_crown_result_three, value = "Three", MCC = "NCuniform_crown")
NCuniform_crown_coef_stats_four <- generate_stats(result = NCuniform_crown_result_four, value = "Four", MCC = "NCuniform_crown")
NCuniform_crown_coef_stats_all_mod <- rbind(NCuniform_crown_coef_stats_one, NCuniform_crown_coef_stats_two, NCuniform_crown_coef_stats_three, NCuniform_crown_coef_stats_four)

#FBD_stem
FBD_stem_result_one <- choice(result_FBD_stem, "one", boot = 500)
FBD_stem_result_two <- choice(result_FBD_stem, "two", boot = 500)
FBD_stem_result_three <- choice(result_FBD_stem, "three", boot = 500)
FBD_stem_result_four <- choice(result_FBD_stem, "four", boot = 500)

FBD_stem_coef_stats_one <- generate_stats(result = FBD_stem_result_one, value = "One", MCC = "FBD_stem")
FBD_stem_coef_stats_two <- generate_stats(result = FBD_stem_result_two, value = "Two", MCC = "FBD_stem")
FBD_stem_coef_stats_three <- generate_stats(result = FBD_stem_result_three, value = "Three", MCC = "FBD_stem")
FBD_stem_coef_stats_four <- generate_stats(result = FBD_stem_result_four, value = "Four", MCC = "FBD_stem")
FBD_stem_coef_stats_all_mod <- rbind(FBD_stem_coef_stats_one, FBD_stem_coef_stats_two, FBD_stem_coef_stats_three, FBD_stem_coef_stats_four)

#FBD_crown
FBD_crown_result_one <- choice(result_FBD_crown, "one", boot = 500)
FBD_crown_result_two <- choice(result_FBD_crown, "two", boot = 500)
FBD_crown_result_three <- choice(result_FBD_crown, "three", boot = 500)
FBD_crown_result_four <- choice(result_FBD_crown, "four", boot = 500)

FBD_crown_coef_stats_one <- generate_stats(result = FBD_crown_result_one, value = "One", MCC = "FBD_crown")
FBD_crown_coef_stats_two <- generate_stats(result = FBD_crown_result_two, value = "Two", MCC = "FBD_crown")
FBD_crown_coef_stats_three <- generate_stats(result = FBD_crown_result_three, value = "Three", MCC = "FBD_crown")
FBD_crown_coef_stats_four <- generate_stats(result = FBD_crown_result_four, value = "Four", MCC = "FBD_crown")
FBD_crown_coef_stats_all_mod <- rbind(FBD_crown_coef_stats_one, FBD_crown_coef_stats_two, FBD_crown_coef_stats_three, FBD_crown_coef_stats_four)

PA_coef_stats <- rbind(NCuniform_stem_coef_stats_all_mod, NCuniform_crown_coef_stats_all_mod, FBD_stem_coef_stats_all_mod, FBD_crown_coef_stats_all_mod)
write.csv(PA_coef_stats, file = "/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/All_sp_474/Without_transformation/Phylo_PCA/Results/Path_analysis_Global_coef_stats_conditional_avg.csv", row.names = F)
```

```{r Average model path coefficient summaries}

#Function for extracting Path coefficient, SE, and 95% confidence interval from the averaged model results
generate_stats_avg_mods <- function(result, MCC) {
  CS_WP <- c(round(result$coef["Colony_size", "Poly_id"], 2), 
             round(result$se["Colony_size", "Poly_id"], 2), 
             round(result$lower["Colony_size", "Poly_id"], 2), 
             round(result$upper["Colony_size", "Poly_id"], 2))
  
  Climate_WP <- c(round(result$coef["Climate1", "Poly_id"], 2), 
             round(result$se["Climate1", "Poly_id"], 2), 
             round(result$lower["Climate1", "Poly_id"], 2), 
             round(result$upper["Climate1", "Poly_id"], 2))
  
  WP_Climate <- c(round(result$coef["Poly_id", "Climate1"], 2), 
             round(result$se["Poly_id", "Climate1"], 2), 
             round(result$lower["Poly_id", "Climate1"], 2), 
             round(result$upper["Poly_id", "Climate1"], 2))
  
  CS_Climate <- c(round(result$coef["Colony_size", "Climate1"], 2), 
             round(result$se["Colony_size", "Climate1"], 2), 
             round(result$lower["Colony_size", "Climate1"], 2), 
             round(result$upper["Colony_size", "Climate1"], 2))
  
  Climate_CS <- c(round(result$coef["Climate1", "Colony_size"], 2), 
             round(result$se["Climate1", "Colony_size"], 2), 
             round(result$lower["Climate1", "Colony_size"], 2), 
             round(result$upper["Climate1", "Colony_size"], 2))
    
  stats_noname <- as.data.frame(t(data.frame(CS_affects_WP = CS_WP, 
                                             Climate_affects_WP = Climate_WP, 
                                             WP_affects_Climate = WP_Climate, 
                                             CS_affects_Climate = CS_Climate,
                                             Climate_affects_CS = Climate_CS)))
  
  stats <- rename(stats_noname, 
                                 Path_coefficient = V1, 
                                 SE = V2, 
                                 Lower_95_CI = V3, 
                                 Upper_95_CI = V4)
  
  # Add the column "MCC" to the first position
  stats <- mutate(stats, Tree := MCC)
  
  # Add row names to a new column
  stats <- rownames_to_column(stats, var = "Causal_relationship")
  
  return(stats)
}

NCuniform_stem_coef_stats_avg_mod <- generate_stats_avg_mods(result = result_NCuniform_stem_average_conditional, MCC = "NCuniform_stem")
NCuniform_crown_coef_stats_avg_mod <- generate_stats_avg_mods(result = result_NCuniform_crown_average_conditional, MCC = "NCuniform_crown")
FBD_stem_coef_stats_avg_mod <- generate_stats_avg_mods(result = result_FBD_stem_average_conditional, MCC = "FBD_stem")
FBD_crown_coef_stats_avg_mod <- generate_stats_avg_mods(result = result_FBD_crown_average_conditional, MCC = "FBD_crown")

##Combine the four data frames
combined_summaries_avg_mods <- rbind(NCuniform_stem_coef_stats_avg_mod, NCuniform_crown_coef_stats_avg_mod, FBD_stem_coef_stats_avg_mod, FBD_crown_coef_stats_avg_mod)
# write.csv(combined_summaries_avg_mods, file = "/Users/louis.bell-roberts/Documents/Github/Division-of-labour/Phylogenetic_analysis/Ant_environmental_data/Analyses/Path_analysis/All_sp_474/Without_transformation/Phylo_PCA/Results/Path_analysis_Global_coef_stats_conditional_avged_models.csv", row.names = FALSE)


```