---
title: "Ant Climate Project"
subtitle: "Path analysis. No transformation"
author: "Louis Bell-Roberts"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
    includes:  
      in_header: preamble-latex.tex
urlcolor: blue
date: \today
---

\tableofcontents
\newpage 

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message=F, warning=F, fig.align='center')
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = T)
# Packages
library(data.table)
library(knitr)
library(ape)
library(ggtree) ## Basic ggplot package for trees
library(ggtreeExtra) ## For fancy tree plotting
library(ufs) ## For ggqq plot
library(phylolm)
library(rr2)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(tibble)
library(phylopath)
library(phylolm)
library(phytools)
theme_set(theme_minimal())
library(kableExtra)
library(stringr)
# global plotting options for histogram
xmin= -7.5
xmax= 0
```

Initial comments:

Read in the ant data and prepare the variables for path analysis. There are 474 species for which data is available for colony size and climatic variables, excluding special ants.
```{r Read in ant data}
ant_data <- read.csv("/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Data/CS/New_transformations/AntClm_CSize_all_230710.csv") #After species with unusual biology removed = 474 species

#Assign rownames as species names
rownames(ant_data) <- ant_data$valid_species_name

#Log transform colony size variable
ant_data$colony.size.y <- log10(ant_data$colony.size.y)

#Assign Poly_id as a factor
ant_data$poly_id <- as.factor(ant_data$poly_id)


#Read in trees
anttree_NCuniform_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_NCuniform_stem_MCC.tre")
anttree_NCuniform_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_NCuniform_crown_MCC.tre")
anttree_FBD_stem <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_FBD_stem_MCC.tre")
anttree_FBD_crown <- read.tree(file = "/Users/louis.bell-roberts/Documents/DTP_1st_project_rotation/Data/Ant_environment/Subsetted/Primary/Trees/CS/474_species/MCC_trees/pruned_474_sp_FBD_crown_MCC.tre")

#Select columns of interest
ant_data_temp_avg_selected <- ant_data %>% dplyr::select(valid_species_name, poly_id, colony.size.y, TMPavg_avg)
ant_data_rain_avg_selected <- ant_data %>% dplyr::select(valid_species_name, poly_id, colony.size.y, PREavg_avg)

#Rename the variables used in the analysis
ant_data_temp_avg_selected_named <- ant_data_temp_avg_selected %>% 
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         TMPavg=TMPavg_avg)

ant_data_rain_avg_selected_named <- ant_data_rain_avg_selected %>%
  rename(Colony_size=colony.size.y,
         Poly_id=poly_id,
         PREavg=PREavg_avg)

```

When more than on climatic variable is present in the best model (based on AIC model selection), we divide the path analysis into multiple different analyses. This is because path analysis would not accept having more than one climatic predictor in the analysis because the linear models produced had highly significant relationships between the multiple climatic predictors being analysed. The potential model set is reduced to just four models for each analysis, based on all of the possible models given that colony size has a direct effect on the number of worker castes.

# Summary
- Greater colony size favours both greater worker size variation and allows invasion into drier regions. Both path coefficients are significant.

# PREavg

## Create alternative causal models
The potential model set is reduced to just two models for each analysis.

```{r Define the potential causal models PREavg, fig.width=10, fig.height=6}
PREavg_models <- define_model_set(
  one = c(Poly_id ~ PREavg, Poly_id ~ Colony_size),
  two = c(PREavg ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ PREavg, Poly_id ~ Colony_size),
  four = c(PREavg ~ Colony_size, Poly_id ~ Colony_size)
)

#PRE model set - 4 models
plot_model_set(PREavg_models, box_x = 22, box_y = 8, text_size = 3.5)

```

## Path analysis
```{r Analyse models PREavg, fig.width=14, fig.height=6}
#Run the models on each of the 4 different MCC trees
PREavg_result_NCuniform_stem <- phylo_path(PREavg_models, data = ant_data_rain_avg_selected_named, tree = anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE", btol = 40)
PREavg_result_NCuniform_crown <- phylo_path(PREavg_models, data = ant_data_rain_avg_selected_named, tree = anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE", btol = 40)
PREavg_result_FBD_stem <- phylo_path(PREavg_models, data = ant_data_rain_avg_selected_named, tree = anttree_FBD_stem, model = "lambda", method = "logistic_MPLE", btol = 40)
PREavg_result_FBD_crown <- phylo_path(PREavg_models, data = ant_data_rain_avg_selected_named, tree = anttree_FBD_crown, model = "lambda", method = "logistic_MPLE", btol = 40)

#Summarise the models
PREavg_result_NCuniform_stem_summary <- PREavg_result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(PREavg_result_NCuniform_stem_summary) <- NULL

PREavg_result_NCuniform_crown_summary <- PREavg_result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
rownames(PREavg_result_NCuniform_crown_summary) <- NULL

PREavg_result_FBD_stem_summary <- PREavg_result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
rownames(PREavg_result_FBD_stem_summary) <- NULL

PREavg_result_FBD_crown_summary <- PREavg_result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
rownames(PREavg_result_FBD_crown_summary) <- NULL

#Produce tables for Rmarkdown
kable(PREavg_result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(PREavg_result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(PREavg_result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(PREavg_result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")

#Plot model summaries
# plot(summary(PREavg_result_NCuniform_stem))
# plot(summary(PREavg_result_NCuniform_crown))
# plot(summary(PREavg_result_FBD_stem))
# plot(summary(PREavg_result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage
PREavg_average_model_full_NCuniform_stem <- average(PREavg_result_NCuniform_stem, avg_method = "full")
PREavg_average_model_full_NCuniform_crown <- average(PREavg_result_NCuniform_crown, avg_method = "full")
PREavg_average_model_full_FBD_stem <- average(PREavg_result_FBD_stem, avg_method = "full")
PREavg_average_model_full_FBD_crown <- average(PREavg_result_FBD_crown, avg_method = "full")

#Plot
plot(PREavg_average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(PREavg_average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(PREavg_average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(PREavg_average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
```

### Estimate confidence intervals for path coefficients
```{r Analyse models PREavg - path coefficients CI, fig.width=14, fig.height=2}
#Estimate confidence intervals for path coefficients
##NCuniform_stem
# PREavg_CI_four_NCuniform_stem <- choice(PREavg_result_NCuniform_stem, "four", boot = 500)

##NCuniform_crown
# PREavg_CI_four_NCuniform_crown <- choice(PREavg_result_NCuniform_crown, "four", boot = 500)

##FBD_stem
# PREavg_CI_four_FBD_stem <- choice(PREavg_result_FBD_stem, "four", boot = 500) #Significant relationship between CS and PRE

##FBD_crown
# PREavg_CI_four_FBD_crown <- choice(PREavg_result_FBD_crown, "four", boot = 500)

#Print out the tables and plots
##NCuniform_stem
###Individual models
# PREavg_CI_three_NCuniform_stem
# PREavg_CI_four_NCuniform_stem
###Averaged model
coef_plot(PREavg_average_model_full_NCuniform_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##NCuniform_crown
###Individual models
# PREavg_CI_four_NCuniform_crown
###Averaged model
coef_plot(PREavg_average_model_full_NCuniform_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_stem
###Individual models
# PREavg_CI_four_FBD_stem
###Averaged model
coef_plot(PREavg_average_model_full_FBD_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_crown
###Individual models
# PREavg_CI_three_FBD_crown
# PREavg_CI_four_FBD_crown
###Averaged model
coef_plot(PREavg_average_model_full_FBD_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```

# TMPavg

## Create alternative causal models
```{r Define the potential causal models TMPavg, fig.width=10, fig.height=6}
### The final set of path models ###
#Define the models for the analysis: response before the ~, effector after the ~

TMPavg_models <- define_model_set(
  one = c(Poly_id ~ TMPavg, Poly_id ~ Colony_size),
  two = c(TMPavg ~ Poly_id, Poly_id ~ Colony_size),
  three = c(Colony_size ~ TMPavg, Poly_id ~ Colony_size),
  four = c(TMPavg ~ Colony_size, Poly_id ~ Colony_size)
)

#TMP model set - 4 models
plot_model_set(TMPavg_models, box_x = 22, box_y = 8, text_size = 3.5)
```


## Path analysis
```{r Analyse models TMPavg, fig.width=14, fig.height=6}
#Run the models on each of the 4 different MCC trees
TMPavg_result_NCuniform_stem <- phylo_path(TMPavg_models, data = ant_data_temp_avg_selected_named, tree = anttree_NCuniform_stem, model = "lambda", method = "logistic_MPLE", btol = 30)
TMPavg_result_NCuniform_crown <- phylo_path(TMPavg_models, data = ant_data_temp_avg_selected_named, tree = anttree_NCuniform_crown, model = "lambda", method = "logistic_MPLE", btol = 30)
TMPavg_result_FBD_stem <- phylo_path(TMPavg_models, data = ant_data_temp_avg_selected_named, tree = anttree_FBD_stem, model = "lambda", method = "logistic_MPLE", btol = 30)
TMPavg_result_FBD_crown <- phylo_path(TMPavg_models, data = ant_data_temp_avg_selected_named, tree = anttree_FBD_crown, model = "lambda", method = "logistic_MPLE", btol = 30)


#Summarise the models
TMPavg_result_NCuniform_stem_summary <- TMPavg_result_NCuniform_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)
 #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(TMPavg_result_NCuniform_stem_summary) <- NULL

TMPavg_result_NCuniform_crown_summary <- TMPavg_result_NCuniform_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2)  #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(TMPavg_result_NCuniform_crown_summary) <- NULL

TMPavg_result_FBD_stem_summary <- TMPavg_result_FBD_stem %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2) #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(TMPavg_result_FBD_stem_summary) <- NULL

TMPavg_result_FBD_crown_summary <- TMPavg_result_FBD_crown %>% summary() %>% as.data.frame() %>% select(2:9) %>% round(digits = 2) %>% mutate(model = row.names(.)) %>% select(model, everything()) %>% rename("CICc difference" = delta_CICc) %>% filter(`CICc difference` <= 2) #k=number of conditional independencies tested; q=number of parameters estimated; l=likelihood; w=CICc weight
rownames(TMPavg_result_FBD_crown_summary) <- NULL




#Produce tables for Rmarkdown
kable(TMPavg_result_NCuniform_stem_summary, caption = "NCuniform stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position") #The kableExtra chunk of code holds the table in position so that it does not start floating around the document
kable(TMPavg_result_NCuniform_crown_summary, caption = "NCuniform crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(TMPavg_result_FBD_stem_summary, caption = "FBD stem path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
kable(TMPavg_result_FBD_crown_summary, caption = "FBD crown path analysis model selection summary table") %>%
  kableExtra::kable_styling(latex_options = "hold_position")


#Plot model summaries
# plot(summary(TMPavg_result_NCuniform_stem))
# plot(summary(TMPavg_result_NCuniform_crown))
# plot(summary(TMPavg_result_FBD_stem))
# plot(summary(TMPavg_result_FBD_crown))

#Perform model averaging - 'full' allows shrinkage
TMPavg_average_model_full_NCuniform_stem <- average(TMPavg_result_NCuniform_stem, avg_method = "full")
TMPavg_average_model_full_NCuniform_crown <- average(TMPavg_result_NCuniform_crown, avg_method = "full")
TMPavg_average_model_full_FBD_stem <- average(TMPavg_result_FBD_stem, avg_method = "full")
TMPavg_average_model_full_FBD_crown <- average(TMPavg_result_FBD_crown, avg_method = "full")

#Plot
plot(TMPavg_average_model_full_NCuniform_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(TMPavg_average_model_full_NCuniform_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(TMPavg_average_model_full_FBD_stem, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)
plot(TMPavg_average_model_full_FBD_crown, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5)

# plot(TMPavg_average_model_full)
# plot(average_model_full, algorithm = 'mds', curvature = 0.1, box_x = 10, box_y = 10, text_size = 5, labels = c(Queen_number = "QN", Mating_frequency = "MF", Colony_size = "CS", Caste_number = "CN"))
# summary(phylolm(Colony_size ~ Rain_avg + DTR_avg + Temp_sd, phy = anttree_NCuniform_stem, data = ant_data_selected_named, model = "lambda"))
# summary(phylolm(Temp_sd ~ DTR_avg, phy = anttree_NCuniform_stem, data = ant_data_selected_named, model = "BM"))
# summary(lm(Temp_sd ~ DTR_avg, data = ant_data_selected_named))
# plot(ant_data_selected_named$Temp_sd, ant_data_selected_named$DTR_avg)
```

### Estimate confidence intervals for path coefficients
```{r Analyse models TMPavg - path coefficients CI, fig.width=14, fig.height=2}
#Estimate confidence intervals for path coefficients
##NCuniform_stem
# TMPavg_CI_four_NCuniform_stem <- choice(TMPavg_result_NCuniform_stem, "four", boot = 500)

##NCuniform_crown
# TMPavg_CI_four_NCuniform_crown <- choice(TMPavg_result_NCuniform_crown, "four", boot = 500)

##FBD_stem
# TMPavg_CI_four_FBD_stem <- choice(TMPavg_result_FBD_stem, "four", boot = 500) #Significant relationship between CS and PRE

##FBD_crown
# TMPavg_CI_four_FBD_crown <- choice(TMPavg_result_FBD_crown, "four", boot = 500)

#Print out the tables and plots
##NCuniform_stem
###Individual models
# TMPavg_CI_three_NCuniform_stem
# TMPavg_CI_four_NCuniform_stem
###Averaged model
coef_plot(TMPavg_average_model_full_NCuniform_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##NCuniform_crown
###Individual models
# TMPavg_CI_four_NCuniform_crown
###Averaged model
coef_plot(TMPavg_average_model_full_NCuniform_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_stem
###Individual models
# TMPavg_CI_four_FBD_stem
###Averaged model
coef_plot(TMPavg_average_model_full_FBD_stem, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)

##FBD_crown
###Individual models
# TMPavg_CI_three_FBD_crown
# TMPavg_CI_four_FBD_crown
###Averaged model
coef_plot(TMPavg_average_model_full_FBD_crown, error_bar = "ci", reverse_order = TRUE) +
  ggplot2::coord_flip() +
  ggplot2::theme_bw(base_size = 17)
```